\documentclass{article}
\begin{document}
ID: 199703003019
Content:
a) Given that \[x^{2} - 2xy + 2y^{2} = 4\], find an expression for \[\frac{\mathrm{d} y}{\mathrm{d} x}\] in terms of x and y. Find the coordinates of each point on the curve \[x^{2} - 2xy + 2y^{2} = 4\] at which the tangent is parallel to the x-axis.;;b) A curve is defined by the parametric equations \[x = t^{2}, y = t^{3}\]. Show that the equation of the tangent to the curve at the point \[P(p^{2}, p^{3})\] is \[2y - 3px + p^{3} = 0\]. Show that there is just one point on the curve at which the tangent passes through the point (-3, -5), and determine the coordinates of this point.Answers:
36: \frac{dy}{dx} = "\frac{x-y}{x-2y}".
37: Coordinates are ("2","2") and ("-2","-2").
38: 
39: 
40: Coordinate of the point at which the tangent passes through the point (-3, -5) = ("1","1").

ID: 199804003011
Content:
a) The curve C has polar equation \[r = \frac {a}{\theta}\], for \[0 < \theta \leq 2\pi\],  where a is a positive constant. Give a reason why, if r is large, \[r\sin \theta \approx a\].Deduce the cartesian equation of the asymptote of C.Sketch C. Find the area of the sector bounded by C and the lines \[\theta = \frac {1}{2} \pi\] and \[\theta = \frac {3}{2} \pi\].;;b) The cartesian equation of a curve is \[3(x - 1)^2 + 4y^2 = 12\]. Show that \[-1 \leq x \leq 3\], and find the range of possible values of y. Find the polar equation of this curve, expressing r in terms of \[\theta\].Answers:

ID: 199804003013
Content:
a) Find the general solution of the differential equation \[\frac{\mathrm{d} y}{\mathrm{d} x} + 3x(y^2 + 4) = 0\], expressing y in terms of x.;;b) Find the value of the constant a such that \[y=axe^{3x}\] is a particular integral of the differential equation ;\[\frac{\mathrm{d}^2 y}{\mathrm{d} x^2} + \frac{\mathrm{d} y}{\mathrm{d} x} - 12y = 7e^{3x}\]. Solve the differential equation given that when x = 0, y = 3 and \[\frac{\mathrm{d} y}{\mathrm{d} x} = - 4\].Answers:
159: General solution of the differential equation \frac{dy}{dx} + 3x(y^2 + 4) = 0, expressing y in terms of x. Therefore y = "2 \tan{(- 3{x}^{2} + c)}".

ID: 199904003014
Content:
a) Solve the differential equation \[\frac{\mathrm{d}^2 y}{\mathrm{d} x^2} + 2\frac{\mathrm{d} y}{\mathrm{d} x} + y = x\], given that, when x = 0, y = -2 and \[\frac{\mathrm{d} y}{\mathrm{d} x} = -2\].;;b) Use the substitution y = u - 2x to find the general solution of the differential equation \[\frac{\mathrm{d} y}{\mathrm{d} x} = \frac {8x + 4y + 1}{4x + 2y + 1}\].Answers:
238: General solution of the differential question \frac{dy}{dx} = \frac{8x+4y+1}{4x+2y+1} is x = "(2x+y)^2+(2x+y)".

ID: 200004003013
Content:
Solve the following differential equations, given in each case that y = 1 when x = 0. Give your answers in a form expressing y in terms of x. ;;a)$$\frac{dy}{dx} = 2x + 2xy^2 $$. ;;b)$$( 1 + x^2 )\frac{dy}{dx} + 4xy = \frac{4x}{( 1 + x^2  )^3}$$.Answers:
313: y = "\tan{(x^2 + \frac{\pi}{4})}".
314: y = "\frac{2}{(1+x^2)^3} + \frac{3}{(1+x^2)^2}".

ID: 200104003014
Content:
a)  Find the general solution of the differential equation  $$x\frac{dy}{dx} + 3y = 5x^2 $$, expressing y in terms of x. ;;b) A rectangular tank has a horizontal base. Water is flowing into the tank at a constant rate, and flows out at a rate which is proportional to the depth of water in the tank. At time t seconds the depth of water in the tank   is x metres. If the depth is 0.5m, it remains at this constant value. Show that $$ \frac{dx}{dt} =  - k( 2x - 1 )$$, where k is a positive constant. When t = 0, the depth of water in the tank is 0.75m and is decreasing at a rate of  $$0.001ms^{- 1}$$. Find the time at which the depth of water is 0.55m.  Answers:
407: y = "x^2 + \frac{C}{x^3}".
408: 
409: Water is 0.55m at "40.2".

ID: 200203003008
Content:
Find the general solution of the differential equation  $$(1 - x^2)\frac{dy}{dx}- xy = 1$$,  $$| x | < 1$$. Answers:
430: General solution = "\frac{\sin^{-1} {x}}{\sqrt{1-x^2}}".

ID: 200303003015
Content:
The variables x and y are related by the differential equation  $$\frac{dy}{dx}+\frac{y}{x} = y^3 $$. ;(i) State clearly why the integrating factor method cannot be used to solve this equation. ;(ii) The variables y and z are related by the equation  $$\frac{1}{y^2} = -2z$$. Show that  $$\frac{dz}{dx} - \frac{2z}{x} = 1$$. ;(iii) Find the solution of the differential equation  $$\frac{dy}{dx} + \frac{y}{x} = y^3 $$, given that y = 2 when x = 1.  Answers:
516: 
517: 
518: y^2 = "\frac{4}{x(8-7x)}".

ID: 200403003015
Content:
Show that the substitution  $$z = \frac{1}{y^2}$$ reduces the differential equation  $$\frac{dy}{dx}+y = xy^3 $$ to  $$\frac{dz}{dx}-2z = -2x$$. Hence find the general solution of the differential equation  $$\frac{dy}{dx} + y = xy^3 $$. Find the particular solution for which  $$y = \sqrt 2 $$ when $$x = 0$$, giving your answer in the form $$y = f(x)$$.  Answers:
575: 
576: General solution of the differential equation is \frac{1}{y^2} = "\frac{1}{2} + x + ce^{2x}".
577: Particular solution is y = "\sqrt{\frac{2}{1+2x}}".

ID: 200503003010
Content:
Show that the substitution $$y^2 = \frac{1}{z}$$ reduces the differential equation $$x\frac{dy}{dx} + y = x y^3$$  to the differential equation $$\frac{dz}{dx} - \frac{2z}{x} = - 2$$ Hence find the general solution of the differential equation $$x\frac{dy}{dx} + y = xy^{3}$$ Answers:
625: 
626: General solution of the differential equation is y^2 = "\frac{1}{2x+cx^2}".

\end{document}
