\documentclass{article}
\begin{document}
ID: 199803003006
Content:
In this question, a 'word' is defined to be any set of letters in a row, whether or not it makes sense. ;Find how many different 'words' can be made using all 8 letters of the word SYLLABUS. Answers:
87: No. of ways to arrange 8 letters including 2 S's and 2 L's = "10080".

ID: 199903003018
Content:
a) Eight people go to the theatre and sit in a particular group of eight adjacent reserved seats in the front row. Three of the eight belong to one family and sit together.;(i) If the other five people do not mind where they sit, find the number of possible seating arrangements for all eight people.;(ii) If the other five people do not mind where they sit, except that two of them refuse to sit together, find the number of possible seating arrangements for all eight people.;;b) The salad bar at a restaurant has 6 separate bowls containing lettuce, tomatoes, cucumber, radishes, spring onions and beetroot respectively. John decides to visit the salad bar and make a selection. At each bowl, he can choose to take some of the contents or not.;(i) Assuming that John takes some of the contents from at least one bowl, find how many different selections he can make.;(ii) John decides he is going to have 4 salad items, and one of them will be tomatoes. How many different selections can he make?Answers:
196: Total no. of seating arrangements = "4320".
197: Total no. of seating arrangements with the 2 people not sitting together = "2880".
198: No. of different selections (not including the nil combination) = "63".
199: No. of different selections = "10".

ID: 200003003008
Content:
A ten-digit number is formed by writing down the digits 0, 1, 2, 3, 4, 5, 6, 7, 8, 9 in some order. No number is allowed to start with 0. Find how many such numbers are odd.Answers:
253: Total no. of such 10-digit numbers = "1612800".

ID: 200103003007
Content:
In how many ways can a committee of 3 men and 3 women be chosen from a group of 7 men and 6 women? The oldest of the 7 men is A and the oldest of the 6 women is B. It is decided that the committee can include at most one of A and B. In how many ways can the committee now be chosen?Answers:
340: P(no. of ways to form committee of 3 men and 3 women) = "700".
341: P(no. of ways to form committee, the include at most one of A and B) = "550".

ID: 200203003007
Content:
a)  Find the number of different arrangements of the eleven letters of the word ABRACADABRA.;;b) A girl wishes to phone a friend but cannot remember the exact number. She knows that it is a five-digit number, that it is even, and that it consists of the digits 2, 3, 4, 5 and 6 in some order. Using this information, find   the largest number of different wrong telephone numbers she could try. Answers:
428: No of different arrangement = "83160".
429: Largest no. of different wrong telephone numbers she could try = "71".

ID: 200303003004
Content:
A committee of four people is to be chosen from five men and four women. Find the number of ways in which the committee can be chosen;(i) if it consists of two men and two women,;(ii) if it includes at least one man. Answers:
493: No. of ways to choose committee of 2 men and 2 women = "60".
494: No. of ways to choose committee with at least 1 man = "125".

ID: 200403003009
Content:
Find how many positive integers, less than 1000, are;(i) odd numbers,;(ii) odd numbers which are not divisible by 5. Find the sum of the odd numbers, less than 1000, which are not divisible by 5.  Answers:
560: N_{odd} = "500".
561: N_{odd}, not 5 = "400".
562: Sum of the odd numbers, less than 1000, which are not divisible by 5 = "200000".

ID: 200404003004
Content:
img;A rectangular shed, with a door at each end, contains ten fixed concrete bases marked A, B, C, ... , J, five on each side (see diagram). Ten canisters, each containing a different chemical, are placed with one canister on   each base. In how many different ways can the canisters be placed on the bases? Find the number of ways in which the canisters can be placed;(i) if 2 particular canisters must not be placed on any of the 4 bases A, E, F and J next to a door,;(ii) if 2 particular canisters must not be placed next to each other on the same side of the shed. Answers:
581: No. of ways to place 10 canisters on 10 bases = "3628800".
582: No. of ways to place 2 particular canisters (not on any of the 4 bases A, E, F and J next to a door) = "1209600".
583: No. of ways to place 2 particular canisters(not next to each other on the same side of the shed) = "2983680".

ID: 200503003004
Content:
A board of directors consists of 9 men and 4 women, one of whom is Mrs Lee. A committee consisting of 4 people is to be formed from this board of directors and it has been decided that it must contain at least one woman.;(i) How many different committees can be formed?;(ii) How many different committees can be formed that have Mrs Lee as a member? Answers:
612: No. of ways to form committee of 4 people with \geq 1 women = "589".
613: No. of ways to form committee with Mrs Lee selected = "220".

ID: 200603003004
Content:
A box contains 8 balls, of which 3 are identical (and so are indistinguishable from one another) and the other 5 are different from each other. 3 balls are to be picked out of the box  the order in which they are picked out does not matter. Find the number of different possible selections of 3 balls. Answers:
683: No. of different possible selections of 3 balls = "26".

\end{document}
