\documentclass{article}
\begin{document}
ID: 200201001006
Content:
(a)	Calculate the number of different 6-digit numbers which can be formed using the digits 0, 1, 2, 3, 4, 5 without repetition and assuming that a number cannot begin with 0.;(b)	A committee of 4 people is to be chosen from 4 women and 5 men. The committee must contain at least 1 woman. Calculate the number of different committees that can be formed.Answers:

ID: 200204001005
Content:
(a)	The producer of a play requires a total cast of 5, of which 3 are actors and 2 are actresses. He auditions 5 actors and 4 actresses for the cast. Find the total number of ways in which the cast can be obtained.;(b)	Find how many different odd 4-digit numbers less than 4000 can be made from the digits 1, 2, 3, 4, 5, 6, 7 if no digit may be repeated.Answers:

ID: 200302001007
Content:
(a)	Find the number of different arrangements of the letters of word MEXICO.;Find the number of these arrangements;(b)	which begin with M,;(c)	which have the letter X at one end and the letter C at the other end.;Four of the letters of the word MEXICO are selected at random. Find the number of different combinations if;(d)	there is no restriction on the letters selected,;(e)	the letter M must be selected.Answers:

ID: 200304001008
Content:
A garden centre sells 10 different varieties of rose bush. A gardener wishes to buy 6 rose bushes, all of different varieties.;(a)	Calculate the number of ways she can make her selection.;Of the 10 varieties, 3 are pink, 5 are red and 2 are yellow. Calculate the number of ways in which her selection of 6 rose bushes could contain;(b)	no pink rose bush,;(c)	at least one rose bush of each colourAnswers:

ID: 200403001007
Content:
(a)	Find the number of different arrangements of the 9 letters of the word SINGAPORE in which S does not occur as the first letter.;(b)	3 students are selected to form a chess team from a group of 5 girls and 3 boys. Find the number of possible teams that can be selected in which there are more girls than boys.Answers:

ID: 200504001011
Content:
(a)	Each day a new agent sells copies of 10 different newpapers,one of which is The Times. A customer buys 3 different newspapers. Calculate the number of ways the customer can select his newspapers;(i)	If there is no restriction,;(ii)	If 1 of 3 newspapers is The Times.;(b)	Calculate the number of different 5-digit numbers which can be formed using the digits 0,1,2,3,4 without repetition and assumming that a number cannot begin with 0.;How many of these 5-digit numbers are even?Answers:

ID: 200604001010
Content:
(a)	How many different four-digit numbers can be formed from the digits 1,2,3,4,5,6,7,8,9 if no digit may be repeated?;(b)	In a group of 13 entertainers, 8 are singers and 5 are comedians. A concert is to be given by 5 of these entertainers. In the concert there must be at least 1 comedian and there must be more singers than comedians. Find the number of different ways that the 5 entertainers can be selected.Answers:

ID: 200704001008
Content:
(a)	Each of seven cards has on it one of the digits 1,2,3,4,5,6,7; no two cards have the same digit. Four of these cards are selected and arranges to form a 4-digit number.;(i)	How many different 4-digit numbers can be formed in this way?;(ii)	How many of these 4-digit numbers begin and end with an even digit?;(b)	4 people are selected to form a debating team from a group of 5 men and 2 women.;(i)	Find the number of possible teams that can be selected.;(ii)	How many of these contain at least 1 woman?Answers:

\end{document}
