\documentclass{article}
\begin{document}
ID: 199501002023
Content:
Given that A is the point (0, 11), B is the point (8, 5) and O is the origin, calculate;;a) the coordinates of M, the midpoint of AB, [1];;b) the gradient of OM, [1];;c) the length of the line AB, [1];;d) the equation of the line AB. [2]Answers:

ID: 199501002024
Content:
img; The diagram represents the speed-time graph of a cyclist.;;Calculate;;a-i) the speed of the cyclist when t = 16, [1];;a-ii) the distance travelled in the first 35 seconds. [1];;b) After 35 seconds the cyclist stops pedaling. She comes to rest after travelling a further 48 metres. Calculate the time taken for the whole journey. [3]Answers:

ID: 199502002003
Content:
img;The graph shows the relation between the number (n) of units of electricity used and the total cost (c) of an electricity bill.;;a) Use the graph to find;;a-i) the cost of the bill if 300 units are used, [1];;a-ii) the number of units used when the bill is $32.50. [1];;b) Given that the relation is $$C = pn + q$$,;;b-i) state the value of q and explain its significance, [2];;b-ii) find the value of p and explain its significance, [2];;b-iii) find the total cost of the bill if 1100 units are used. [2]Answers:

ID: 199702002010
Content:
img;The diagram shows the speed-time graphs of two objects A and B for the first 10 seconds of their motion. Object A travels at a constant speed of 12 $$ms^{-1}$$ throughout the 10 seconds. Object B starts from rest, attains a speed of 18 $$ms^{-1}$$ after 4 seconds and then travels at constant speed.;;a) Calculate;;a-i) the distance travelled by object B during the first 4 seconds of its motion, [1];;a-ii) the average speed of object B for the first 10 seconds of its motion, [2];;a-iii) after how many seconds object A is travelling at the same speed as object B. [2];;a-iv) after how many seconds both objects have travelled the same distance. [2];;b) (b)	After 10 seconds both objects slow down at the same rate until they come to rest. Given that object A comes to rest after a further 6 seconds, calculate;;b-i) the deceleration of object A. [1];;b-ii) after how many seconds from the start of its motion the object B comes to  rest. [2];;c) In the diagram, the straight line OP and the c;img;Answers:

ID: 199703002011
Content:
img;Which of the above could be the graph of;;a) y = $$\frac{1}{x}$$, [1];;b) y=1-x, [1];;c) y=$$x^2+1?$$ [1]Answers:

ID: 199703002020
Content:
img;The diagram shows the speed-time graph for the first 20 seconds of a cyclist;;a) Calculate the distance travelled in the first 10 seconds. [1];;b) Calculate the total distance travelled in 20 seconds. [1];;c) On the axes in the answer space, draw the distance-time graph for this part of the journey. [2];img;Answers:

ID: 199704002008
Content:
Answer the whole of this question on a sheet of graph paper.;;a) Table I below gives some values of x and the corresponding values of y, correct to two decimal places, where $$y = x(1 + x)(3 - x)$$;;a-i) Find the value of p. [1];;a-ii) Using a scale of 4 cm to represent 1 unit draw a horizontal x-axis for $$0 \leq x \leq 3$$. ;Using a scale of 2 cm to represent 1 unit draw a vertical y-axis for $$0 \leq x \leq 8$$.;On your axes plot the points given in the table and join them with a smooth curve. [3];;a-iii) Use your graph to find the greatest value of $$x(1 + x)(3 - x)$$ in the interval $$0 \leq x \leq 3$$.;;b) Table II shows some corresponding values of x and y where $$y = 2^x$$.;;b-i) Find the value of q, correct to 2 decimal places. [1];;b-ii) On the axes used in part (i)(2) draw the graph of $$y = 2^x$$. [2];;c) From your graphs, find the values of x in the interval $$0 \leq x \leq 3$$, for which [4];;c-i) $$x(1 + x)(3 - x) = 3$$, ;;c-ii) $$x(1 + x)(3 - x) > 2^x$$.Answers:

ID: 199801002019
Content:
img;The diagram is the speed-time graph of a journey.;;a) Calculate;;a-i) the retardation during the last 20 seconds of the journey, [1];;a-ii) the total distance travelled in the 80 seconds. [2];;b) The distance-time graph for $$40\leq t\leq 60$$ is a straight line. State the gradient of this line. [1]Answers:

ID: 199802002006
Content:
a);img;The diagram shows a grid of squares. A button is placed on one of the squares. A fair die is thrown. If 1, 2, 3 or 4 is thrown, the button is moved one square to the left. If 5 or 6 is thrown, the button is moved one square to the right.;;a-i) The button is placed on square X. The die is thrown once. What is the probability that the button is moved to the right? [1];;a-ii) On another occasion the button is placed on square Y. The die is thrown once and the button is moved. The die is thrown a second time and the button is moved again. Find the probability that the button finishes;;a-ii-a) at P, [1];;a-ii-b) at Q, [1];;a-ii-c) at Y, [1];;a-ii-d) at P or Q or Y. [1];;b) It is given that the force (F units) between two particles is inversely proportional to the square of the distance (x units) between them.;;b-i) Which one of the graphs below could represent the relation between the force and the distance? [1];img;;b-ii) What happens to the force when the distance between changes to 2xAnswers:

ID: 199803002010
Content:
img;On the diagram, O is the origin, A is the point (2,1), B is the point (2,7) and C is the point (6,3). The unshaded region R is defined by three inequalities.One of these is $$x + y \leq 9$$;;a) Write down the other two inequalities. [2];;b) Given that the point (x, y) is in the region R, calculate the minimum value of 6x - y. [1]Answers:

ID: 199803002023
Content:
img;The diagram is the speed-time graph for the first k seconds of the motion of an object.;;a) Find the acceleration when t = 10. [1];;b) Find the distance travelled in the first 20 seconds. [1];;c) The distance travelled in the first k seconds is 720 m. Find the value of k. [2];;d) On the axes in the answer space, sketch the distance-time graph for the first k seconds of the motion of the object. [2];img;Answers:

ID: 199804002008
Content:
Answer the whole of this question on a sheet of graph paper. When x copies of a book are produced, the cost, $y, of each copy is given by the formula $$y = 10 + \frac{2400}{x}$$;;a) The table below gives some values of x and the corresponding values of y.;img;;a-i) Find the value of p. [1];;a-ii) Using a scale of 2 cm to represent 200 books, draw a horizontal x-axis for $$0 \leq x \leq 1200$$. Using a scale of 2 cm to represent $5, draw a vertical y-axis for $$0 \leq x \leq 40$$. On your axes plot the points given in the table and join them with a smooth curve. [3];;b) Use your graph to estimate the number of books to be printed if the cost of producing each book is $15. [1];;c-i) By drawing a tangent, find the gradient of the curve at the point where x = 300. [2];;c-ii) Describe briefly what this gradient represents. [1];;d) In order to sell x books, the selling price of each book must be $$(25 - \frac{x}{60})$$ dollars.;;d-i) On the axes used in part (1), draw the graph of $$y = 25 - \frac{x}{60}$$, for values ofAnswers:

ID: 199902002009
Content:
Answer the whole of this question on a sheet of graph paper. A particle was projected directly up a slope. Its distance, d metres, from the bottom of the slope, t seconds after it was projected, it is given in the table below.;img;;;a) Using a horizontal scale of 2 cm to represent 1 second, and a vertical scale of 1 cm to represent 1 metre, draw a graph of d against t. [3];;b) Use your graph to find the distance of the particle from the bottom of the slope when t = 2.5. [1];;c) What happened to the particle after approximately 6 seconds? [1];;d-i) By drawing a tangent, find the gradient of your curve when t = 4. [2];;d-ii) State briefly what this gradient represents. [1];;e) Calculate the average speed of the particle during the first 6 seconds. [1];;f) At the instant the particle was projected, another particle was projected down the slope from point 10 metres from the bottom. This particle moved directly down the slope at a constant speed of 2 m/s.;;f-i) On the same axesAnswers:

ID: 199903002007
Content:
img;The diagram in the answer space shows the line y=mx. On the same diagram, sketch and label;;a) y=mx+2,;;b) y=-mx. [2]Answers:

ID: 199903002023
Content:
img;The diagram is the distance-time graph for the first 22 seconds of a journey.;;a) Find the speed during the first 8 seconds. [1];;b) What is the acceleration when t = 4? [1];;c) Find the average speed from t = 12 to t = 22. [1];;d);img;The speed increases uniformly between t = 12 and t = 22.;The speed is 8 m/s when t = 22.;Sketch the speedAnswers:

ID: 199904002010
Content:
Answer the whole of this question on a sheet of graph paper.;The variables x and y are connected by the equation;$$y = \frac{x^2}{6} + \frac{12}{x} - 6$$;The table below shows some corresponding values of x and y.;img;The values of y are given correct to one decimal place where appropriate.;;a) Calculate the value of k, correct to one decimal place. [1];;b) Using a scale of 2 cm to 1 unit on each axis, draw a horizontal x-axis for $$0 \leq x \leq 8$$  and a vertical y-axis for $$-1 \leq y \leq 7$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;c) By drawing a tangent, find the gradient of the curve at the point (1.5, 2.4). [2];;d) Showing your method clearly, use your graph to find the values of x in the range $$1 \leq x \leq 7$$ for which $$\frac{x^2}{6} + \frac{12}{x} = 7$$ [2];;e-i) On the same axes, draw the graph of the straight line $$y - \frac{x}{4}$$. [2];;e-ii) Using your graphs, find the values of x in the range $$1 \leq x \leq 7$$ for which $$\frac{x^2}{6} + \frac{12}{x} - 6 \leq \frac{x}{4}$$ [2]Answers:

ID: 200001002020
Content:
img;The diagrams above are the speed-time and the distance-time graphs of the same journey.;;a) Calculate;;a-i) the acceleration during the first 20 seconds, [1];;a-ii) the value of k. [2];;b) During the last part of the journey, the retardation is $$3m/s^{2} $$. Calculate the time taken while slowing down. [1]Answers:

ID: 200002002008
Content:
Answer the whole of this question on a sheet of graph paper. The table below gives some values of x and the corresponding values of y, given correct to two decimal places, for $$y=\frac{1}{4}(x^{3} -6x^{2} +8x)$$.;img;;a) Using a scale of 2cm to represent 1 unit on each axis, draw a horizontal x-axis for $$-1\leq x\leq5$$ and a vertical y-axis for $$-4\leq y\leq4$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;b) Describe the symmetry of this curve. [2];;c) Use your graph to solve the equations;;c-i) $$\frac{1}{4}(x^{3} -6x^{2} +8x)=-1$$, [1];;c-ii) $$x^{3} -6x^{2} +8x=8$$. [2];;d) By drawing a tangent, find the gradient of the curve at the origin. [2];;e) The line y = mx intersects the curve $$y=\frac{1}{4}(x^{3} -6x^{2} +8x)$$ at three points. Find the least possible value of m. [2]Answers:

ID: 200003002016
Content:
img;The diagram is the speed-time graph of the first 30 seconds of a journey. Find;;a) the speed when t = 18, [1];;b) the acceleration during the first 10 seconds, [1];;c) the total distance travelled in the 30 seconds. [2]Answers:

ID: 200003002023
Content:
img;The graph shows the charges made by two companies for telephone calls lasting up to 10 minutes. Kingcom charges 40 cents for calls of 3 minutes or less and then at the constant rate of 10 cents per minutes. Phoneshop charges a connection fee of p cents and all calls are charge at the constant rate of q cents per minute. Using these graphs, or otherwise, find;;a) The cost of a 7 minute call using Kingcom, [1];;b) The value of p, [1];;c) The value of q, [1];;d) The range of times for which it would be cheaper to use Kingcom. [2]Answers:

ID: 200004002009
Content:
Answer the whole of this question on a sheet of graph paper.;The table below gives some values of x and the corresponding values of y, correct to two decimal places, where;img;;a-i) Find the value of p and the value of q. [1];;a-ii) Using a scale of 2 cm to 1 unit, draw a horizontal x-axis for $$-1 \leq x \leq 4$$. ;Using a scale of 1 cm to 1 unit, draw a vertical y-axis for $$-2 \leq y \leq 14$$. ;On your axes, plot the points given in the table and join them with a smooth curve. [3];;a-iii) Using your graph, find the values of x for which y = 3. [2];;b) By drawing a tangent, find the gradient of the curve at the point where x = 3. [2];;c) On the axes used in part (1), draw the graph of y = 10 - x for values of x in the range $$-1 \leq x \leq 4$$. [2];;d) Write down, and simplify, the cubic equation which is satisfied by the values of x at the points where the two graphs intersect. [2]Answers:

ID: 200101002013
Content:
img;The diagram below shows the graph of the straight line 2x + y = 4.;;a) Draw the line with equation $$y=\frac{1}{3}x-3$$ on the axes. [2];;b) Solve the simultaneous equations y = -2x + 4, $$y=\frac{1}{3}x-3$$. [1]Answers:

ID: 200101002014
Content:
img;The diagram shows the graph of $$y=2^x$$.;;a) By drawing a tangent, find an estimate of the gradient of this curve at x = 2. [2];;b) Use the graph to find the value of ;;b-i)x when y= $$2^{2.5}$$, [1];;b-ii) n  if $$2^n=5$$. [1]Answers:

ID: 200101002015
Content:
A source of light is observed from a distance of d metres. The amount of light received, L units, is given by the formula $$L=\frac{k}{d^{2}}$$, where k is a constant. Given that L = 9 when d = 2, calculate the value of;;a) k, [1];;b) L when d = 3, [1];;c) d when L = 100. [2]Answers:

ID: 200101002018
Content:
a);img;The diagram shows the distance-time graph for a journey by water-taxi.;;a-i) Calculate, in metres per second,;;a-i-a) the speed during the first 4 minutes, [1];;a-i-b) the average speed for the complete journey. [1];;a-ii) Calculate the time whilst moving as a percentage of the total time taken. [1];;b);img;The first two stages of another journey are shown on the distance-time graph in the answer space. The water-taxi travels from A for 4 minutes. It then stops for 2 minutes to pick up passengers before returning to A in a further 3 minutes. Complete the distance-time graph. [1]Answers:

ID: 200102002008
Content:
img;Answer the whole of this question on a sheet of graph paper. ; The diagram shows a sketch of the curve $$y=36-x^{2} $$. The curve crosses the axes at H, K and L. O is the origin.;;a) Show that the area of triangle OHK is 108 square units. [2];;b) The point P lies on the curve between H and K. The coordinates of P are (x, y). PQRS is a rectangle with Q on the curve and R and S on the x-axis. The area of the rectangle PQRS is A square units. ;;;;Show that $$A=72x-2x^{3} $$. [2];;c) The table below gives some values of x and the corresponding values of A, where $$A=72x-2x^{3} $$.;img;;c-i) Find the value of t. [1];;c-ii) Using a scale of 2 cm to represent 1 unit, draw a horizontal x-axis for $$0\leq x\leq 6$$. Using a scale of 1 cm to represent 20 units, draw a vertical A-axis for $$0\leq A\leq 180$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;c-iii) Use your graph to find the two values of x when A = 108. [2];;c-iv) Find the lengths of the sides of the recAnswers:

ID: 200103002013
Content:
img;The graph of $$y = (x + 2)(3 - x)$$ cuts the x axis at A and B. It cuts the y axis at C. Find;;a) The coordinates of the point C,    [1];;b) The length AB,    [1];;c) The equation of the straight line AC.    [1]Answers:

ID: 200103002015
Content:
y is inversely proportional to (x+2).;;a) Write down an expression for y in terms of x and a constant k.    [1];;b) It is given that y=4 when x=3. Find y when x=8.    [2]Answers:

ID: 200103002019
Content:
a);img;The graph of the line $$y = 2x - 1$$ is shown in the answer space. On the diagram, sketch the graph of;;a-i) y = 2x,;;a-ii) y = 1-2x. [2];;b);img;The point (1, 1) is marked on the diagram in the answer space. On the diagram, sketch the graph of $$y = \frac{1}{x}$$.    [2]Answers:

ID: 200103002022
Content:
A car starts from rest and accelerates at a constant rate to a speed of 20 m/s in 10 seconds.;;a) Find the acceleration.    [1];;b) It then travels at a constant speed of 20m/s for the next 10 seconds. ;Find the total distance travelled in the 20 seconds.    [1];;c) On the axes below, draw;;c-i) the speed-time graph for the first 20 seconds of the car;img;;c-ii) the distance-time graph for the same 20 seconds.    [2];img;Answers:

ID: 200104002009
Content:
img;Answer the whole of this question on a sheet of graph paper.;The table gives some values of x and the corresponding values of y, correct to one decimal place, where $$y = 4x + \frac{25}{x^2}$$;;a) Find the value of p.;;b) Using a scale of 4 cm to represent 1 unit, draw a horizontal x-axis for $$0 \leq x \leq 4$$. ;Using a scale of 4 cm to represent 10 unit, draw a vertical y-axis for $$0 \leq y \leq 30$$.;On your axes, plot the points given in the table and join them with a smooth curve.;;c) Use your graph to find;;c-i) a solution of $$4x + \frac{25}{x^2} = 20$$;;c-ii) the least value of $$4x + \frac{25}{x^2} = 20$$.;;d) By drawing a tangent, find the gradient of the curve at the point where x = 1.5.;;e) On the axes used in part (2), draw the graph of the straight line ; y = 25 ;;f-i) Write down the x coordinates of the points at which the two graphs intersect.;;f-ii) Find the equation, in the form $$ax^3 + bx^2 + cx + d = 0$$, which is satisfied by the values of x found in part (6)(i).Answers:

ID: 200201002020
Content:
img;V varies inversely as P. When P = 3, V = 1. ;;a) Express V in terms of P. [2];;b) Complete the table. [2]Answers:

ID: 200201002022
Content:
img;The diagram shows the speed-time graph of a bus over a period of 90 seconds. The bus reaches a maximum speed of 15 metres per second.;;a) Express 15 metres per second in kilometers per hour. [1];;b) Given that the acceleration was $$0.5 ms^{-2} $$, calculate the time taken, in seconds, to reach its maximum speed. [1];;c) The total distance travelled during the 90 seconds was 750 metres. Calculate the length of time that the bus was travelling at its maximum speed. [2]Answers:

ID: 200202002008
Content:
Answer the whole of this question on a sheet of graph paper. ; The table below gives some values of x and the corresponding values of y, where $$y=30-18x+x^{3} $$.;img;;a) Using a scale of 2 cm to represent 1 unit, draw a horizontal x-axis for $$-4\leq x\leq4$$. Using a scale of 2 cm to represent 10 units, draw a vertical y-axis for $$0\leq y\leq 60$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;b) Use your graph to find;;b-i) the largest value of  $$30-18x+x^{3}$$ in the interval $$-4\leq x\leq 4$$, [1];;b-ii) the smallest value of x for which $$30-18x+x^{3} =50$$. [1];;c) By drawing a tangent, find the gradient of the curve when x = 1. [2];;d) A is the point (0, 27) and B is the point (3, 3).;;d-i) Draw, on the axes used in part (a), the line which passes through A and B. [1];;d-ii) Find the equation of AB. [2];;d-iii) The x coordinates of the points where the line AB intersects the curve are the solutions of the equation $$x^{3} +ax+b=0$$. Find the value of a and bAnswers:

ID: 200203002017
Content:
a) The sketch represents the graph of $$y = x^n$$. Write down a possible value of n.   [1];;b) The point (1, 1) is marked on each diagram in the answer space. On these diagrams, sketch the graphs of;;b-i) $$y = \frac{1}{3}x + 1$$,   [1];;b-ii) $$y = \frac{1}{x^2}$$,   [1];;b-iii) $$y = 2^x$$.   [1]Answers:

ID: 200203002019
Content:
The force of attraction between two magnets if F Newtons.;This force is inversely proportional to the square of the distance, d centimeters, between the magnets.;;a) When the magnets are a certain distance apart, the force is 10 Newtons. What is the force when this distance is doubled?   [1];;b-i) Write down a formula connecting F, d and a constant k.   [1];;b-ii) When the magnets are 3 cm apart, the force is 2 Newtons. Find the force when they are 5 cm apart.   [2]Answers:

ID: 200203002020
Content:
img;The diagram is the speed-time graph of a car;;a) the speed when t = 6,   [1];;b) the acceleration when t = 6,   [1];;c) the distance travelled in the first 20 seconds,   [1];;d) the value of t when the retardation is greatest.   [1]Answers:

ID: 200203002024
Content:
img;A rectangular piece of card measures 20 cm by 14 cm. Squares of side x cm are cut from the four corners and the card is folded to make an open box.;;a) Show that the volume, $$V cm^3$$, if the box is given by $$V = 4x(10 - x)(7 - x)$$ [1];;b) You are asked to find the value of x which will produce the greatest volume of the box. You should use the table and the grid to help you in your investigation. Marks will be awarded for clear working.   [4];img;Answers:

ID: 200204002003
Content:
a) The points A and B are (-2, 1) and (6, -5) respectively. Calculate;;a-i) the gradient of the line AB,   [1];;a-ii) the equation of the line through A and B.   [2];;b) The points C and D are (4, 5) and (p, q) respectively.;;b-i) Write down, in terms of p and q, the coordinates of the midpoint of CD.   [1];;b-ii) Given that the midpoint of CD is (7, 1), find the coordinates of D.   [2]Answers:

ID: 200204002010
Content:
Answer the whole of this question on a sheet of a graph paper.;;;A man stood at the top of a tower.;;;He threw a ball vertically upwards.;;;The height, h metres, of the ball above the top of the tower at a time t seconds after it was thrown is given by the formula $$h = 22t - 4.9t^2$$;;;The table below shows some values of t and the corresponding values of h, correct to 1 decimal place.;img;;a) Explain the significance of the value h = -12.5 when t = 5.   [1];;b) Find the value of p.   [1];;c) Using a scale of 2 cm to 1 second, draw a horizontal t-axis for $$0 \leq t \leq 6$$.;Using a scale of 2 cm to 10 metres, draw a vertical h-axis for $$-50 \leq h \leq 30$$.;On your axes, plot the points given in the table and join them with a smooth curve.   [3];;d) Use your graph to find;;d-i) the greatest height of the ball above the top of the tower,   [1];;d-ii) the length of time for which the ball was more than 20 metres above the top of the tower.   [2];;e-i) By drawing a tangent atAnswers:

ID: 200301002024
Content:
img;The speed-time graph shows the performance of a cyclist during the first 90 seconds of a race.;;a) Calculate the acceleration of the cyclist during the first 10 seconds. [1];;b) Calculate the distance, in meters, travelled by the cyclist in the first 90 seconds. [3];;c) Calculate the time taken for the cyclist to travel 1 kilometer. [2]Answers:

ID: 200302002008
Content:
Answer the whole of this question on a sheet of graph paper.;;Temperatures were recorded over a nine hour period. The table below shows the temperature, $$y ^{\circ}C$$, at various times.;img;;a) Using a scale of 1 cm to represent 1 hour, draw a horizontal x-axis for $$0\leq x\leq 9$$. Using a scale of 2 cm to represent $$1^{\circ}C$$, draw a vertical y-axis for $$-2\leq y\leq 4$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;b) Use your graph to find an estimate for;;b-i) the temperature when x = 5.5, [1];;b-ii) the difference between the highest and lowest temperatures, [1];;b-iii) how long, in hours and minutes, the temperature was above $$2^{\circ}C$$. [2];;c-i) By drawing a tangent, find the gradient of the curve at that point where x = 8. [2];;c-ii) State briefly what this gradient represents. [1];;d) The curve from x = 0 to x = 2 has the equation $$y=x^{2} +Bx+C$$. Find the value of C and the value of B. [2]Answers:

ID: 200304002009
Content:
Answer the whole of this question on a sheet of graph paper.;An open rectangular tank has a square base of side x metres.;The volume of the tank is $$36 m^3$$.;;a-i) Find an expression, in terms of x,for the height of the tank.   [1];;a-ii) Hence show that the total external surface area of the tank, A square metres, is given by $$A = x^2 + \frac{144}{x}$$ [1];;b) The table below shows some values of x and the corresponding values of A, ;Correct to 1 decimal place, where $$A = x^2 + \frac{144}{x}$$.;img;;b-i) Find the value of p.   [1];;b-ii) Using a scale of 2 cm to 1 metre, draw a horizontal x-axis for $$2 \leq x \leq 8$$. ;Using a scale of 2 cm to $$10 m^2$$, draw a vertical A-axis for $$40 \leq A \leq 90$$.;On your axes, plot the points given in the table and join them with a smooth curve.   [3];;b-iii) Use your graph to find;;b-iii-a) The values of x for which the surface area is $$65 m^2$$,   [2];;b-iii-b) The gradient of the curve at x = 6,   [2];;b-iii-c) The dimensions of the minimal AAnswers:

ID: 200403002011
Content:
img;The diagram shows the graph of $$y= x^{2} + x -12$$.;;a) The graph cuts the y-axis at K(0, k). Write down the value of k. [1];;b) The graph cuts the x-axis at L(l, 0) and M(m, 0). Find the value of;;b-i) l, [1];;b-ii) m. [1]Answers:

ID: 200403002015
Content:
a) p is proportional to $$q^{3} $$. It is known that p = 24 for a particular value of q. Find the value of p when this value of q is halved. [1];;b) y is inversely proportional to $$x^{2} $$. y = 4 when x = 3. Find y when x = 10. [2]Answers:

ID: 200403002021
Content:
img;The diagram shows the distance-time graphs of the journeys of Ali and Bala from home to school. They leave home together and follow the same route. Ali runs to school and Bala cycles.;;a) How long does it take Ali to run the first 700 m? [1];;b) Estimate the distance between Ali and Bala when t = 3. [1];;c) Find Bala;;d) Find BalaAnswers:

ID: 200503002009
Content:
img;Which of the graphs shown above could be the graph of;;a) $$y=x^{3} $$ ,  [1];;b) $$y=\frac{1}{x^{2}}$$, [1];;c) y = x - 1? [1]Answers:

ID: 200503002020
Content:
img;The diagram shows the speed-time graph of a car;;a) Find the speed when t = 20. [1];;b) Find the acceleration when t = 20. [1];;c) Find the distance travelled in;;c-i) the first 40 seconds, [1];;c-ii) the first 60 seconds. [1];;d) Part of the distance-time graph for the same journey is shown in the answer space. Complete this graph. [2];img;Answers:

ID: 200504002010
Content:
img;Answer the whole of this question on a sheet of graph paper.;;The area of a rectangular garden, ABCD, is $$100 m^2$$;;a) Taking the length of AB to be x metres, write down expressions, in terms of x, for;;a-i) EF,;;a-ii) BC,;;a-iii) FG. [2];;b) Hence show that the area, y square metres, of the lawn, EFGH is given by $$y=110-5x-\frac{200}{x}$$. [1];;c) The table below shows some values of x and the corresponding values of y, correct to 1 decimal place, where $$y=110-5x-\frac{200}{x}$$. Find the value of p. [1];img;;d) Using a scale of 2 cm to 1 metre, draw a horizontal x-axis for $$4\leq x\leq 10$$. Using a scale of 2 cm to 2 square metres, draw a vertical y-axis for $$40\leq y\leq 48$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;e) By drawing a tangent, find the gradient of the curve where x = 8. [2];;f) Use your graph to find;;f-i) the range of values of x for which the area of the lawn is at least $$44 m^{2} $$, [2];;f-ii) the value of Answers:

ID: 200603002017
Content:
a) y is proportional to $$x^{n}$$. Write down the value of n when;;a-i) $$y cm^{2} $$ is the area of a circle of radius x cm, [1];;a-ii) y hours is the time taken to travel a distance x km at a constant speed. [1];;b) The force, F, between two particles is inversely proportional to the square of the distance between them. The force is 36 units when the distance between the particles	is r metres. Find the force when the distance is 3r metres. [2]Answers:

ID: 200603002021
Content:
img;The diagram is the speed-time graph for the first 20 seconds of a journey.;;a) Find;;a-i) the acceleration when t = 16, [1];;a-ii) the distance travelled in the first 20 seconds. [1];;b) On the grid in the answer space, sketch the distance-time graph for the same journey. [3];img;Answers:

ID: 200604002010
Content:
Answer the whole of this question on a sheet of graph paper. ;; The variable x and y are connected by the equation $$y=\frac{x^{2}}{5}+\frac{5}{x}$$. The table below shows some values of x and the corresponding values of y correct to 1 decimal place.;img;;a) Calculate the value of p. [1];;b) Using a scale of 2 cm to represent 1 unit on each axis, draw a horizontal x-axis for $$0\leq x\leq 6$$ and a vertical y-axis for $$0\leq y\leq 9$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;c) Use your graph to find the values of x in the range $$1\leq x\leq 6$$ for which $$\frac{x^{2}}{5}+\frac{5}{x}-4=0$$. [2];;d) By drawing a tangent, find the gradient of the curve at the point (4, 4.5). [2];;e-i) On the same axes, draw the graph of $$y=\frac{1}{2}x+3$$. [2];;e-ii) Write down the x coordinates of the points at which the two graphs intersect. [1];;e-iii) Find the equation, in the form $$2x^{3} +ax^{2} +bx+c=0$$, which is satisfied by the values of x found in part (e)(ii). [1]Answers:

ID: 200703002017
Content:
img;The diagram is the distance-time graph for the first 25 seconds of a car;;a) Find the speed of the car when t = 15. [1];;b) The car moved with a constant acceleration for the first 10 seconds. Find this acceleration. [1];;c) On the grid in the answer space, draw the speed-time graph for the same journey. [2];img;Answers:

ID: 200703002018
Content:
img;a)The graph of $$y=3-12x^{2} $$ intersects the y-axis at A and the x-axis at B and C. Write down the coordinates of A, B and C. [2];;b);img;The sketch represents the graph of y = $$x^{n}$$. Write down a possible value of n. [1];;c) Write down a possible equation for this graph. [1]Answers:

ID: 200703002019
Content:
The force of attraction, F newtons, between two magnets is inversely proportional to the square of the distance, x centimeters, between them.;;a) When the magnets are 4 cm apart, the force is 3 newtons. Find the formula connection F and x. [2];;b) Find the force when the magnets are 2 cm apart. [1];;c) When the magnets are a certain distance apart, the force is 1.25 newtons. Write down the force when the distance is halved. [1]Answers:

ID: 200704002010
Content:
img;Answer the whole of this question on a sheet of graph paper. A stone was thrown from the top of a vertical tower. Its position during the flight is represented by the equation $$y=50+21 x-x^{2}$$, where y metres is the height of the stone above the ground and x metres is its horizontal distance from the foot of the tower.;;a-i) Solve the equation $$0=50+21x-x^{2}$$, giving both answers correct to one decimal place. [4];;a-ii) Explain briefly what the positive solution of this equation represents [1];;b) Some corresponding values of x and y are given in the following table. Using a scale of 2 cm to represent 5 metres, draw a horizontal x-axis for $$0\leq x\leq 25$$. Using a scale of 2 cm to represent 20 metres, draw a vertical y-axis for $$0\leq y\leq 180$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;c) Use your graph to find the greatest height reached by the stone. [1];;d-i) By drawing a tangent, find the gradient of the graph at the point where x = 16. [2]Answers:

ID: 200803002020
Content:
Alan left home at 0800 and cycled 20 km to a sports centre. He later returned home. The diagram below is Alan;img;;a) Calculate his speed on the journey from home to the sports centre.;;b) How far from the sports centre was he at 0940?;;c) Alan;;c-i) On the same axes, draw the graph to represent Brenda;;c-ii) At what time did Brenda pass Alan on the return journey?Answers:

ID: 200803002022
Content:
a-i) Sketch the graph of y = x(3 - x);img;;a-ii) Write down the equation of the line of symmetry of y = x(3 - x);;b-i) Sketch the graph of $$y = (x + 2)^2 - 1$$.;img;;b-ii) Write down the coordinates of the minimum point of the curve.Answers:

ID: 200804002009
Content:
Answer the whole of this question on a sheet of graph paper. ; The variables x and y are connected by the equation ; $$y = \frac{1}{5}x(12 - x^2)$$ ; Some corresponding values of x and y are given in the following table. ;img;;a) Find the value of p.;;b) Using a scale of 2 cm to 1 unit, draw a horizontal x-axis for $$-3 \leq x \leq 4$$. ; Using a scale of 2 cm to 1 unit, draw a vertical y-axis for $$-4 \leq y \leq 4$$ ; On your axes, plot the points given in the table and join them with a smooth curve.;;c) Use your graph to find two solutions of $$\frac{1}{5}x(12 - x^2) = 1$$ in the range $$-3 \leq x \leq 4$$.;;d) By drawing a tangent, find the gradient of the curve at the point (3, 1.8).;;e) On the same axes, draw the graph of 2x = y = 2 for $$-1 \leq x \leq 3$$.;;f-i) Write down the x coordinate of the point where the two graphs intersect.   [1];;f-ii) This value of x is a solution of the equation $$x^3 + Ax + Bx + X = 0$$. ; Find the value of A, the value of B and the value of C.Answers:

ID: 200904002006
Content:
Answer the whole of this question on a sheet of graph paper. ; The variables x and y are connected by equation y = $$\frac{1}{10} (60 - x^2 - \frac{80}{x})$$. ; Some corresponding values of x and y, correct to 2 decimal places are given in the table below.;img;;a) Calculate the value of p.;;b) Using a scale of 2 cm to represent 1 unit on each axis, draw a horizontal x-axis for $$1 \leq x \leq 6$$ and a vertical y-axis for $$-3 \leq y \leq 3$$. ; On your axes, plot the points given in the table and join them with a smooth curve.;;c) Use your graph to find the values of x in $$1 \leq x \leq 6$$ for which $$\frac{1}{10}(60 - x^2 - \frac{80}{x}) = 2$$;;d) By drawing a tangent, find the gradient of the curve at (1.5, 0.44).;;e) Use your graph to find the largest value of y in $$1 \leq x \leq 6$$ and the value of x for which this occurs.Answers:

ID: 201003002013
Content:
The volume, V, of a given mass of gas is inversely proportional to the pressure, P. ; When V = $$3 m^3$$, P = $$200 Nm^{-2}$$;;a) Find V when P = $$150 Nm^{-2}$$;;b) Find the pressure when the volume is $$5 m^3$$Answers:

ID: 201003002017
Content:
img;The graph shows Alison;;a) How long did she wait at the bus stop?;;b) How far was she from school at 08 15?;;c) Find the speed of the bus.;;d) AlisonAnswers:

ID: 201003002018
Content:
Twenty boys and fifteen girls took a Mathematics test. ; The marks are shown in the stem and leaf diagram.;img;;a) Write down the mode of the boy;;b) Write down the median of the girls;;c) Explain briefly whether the boys or the girls performed better in the rest.Answers:

ID: 201004002009
Content:
Answer the whole of this question on a sheet of graph paper. ; Elizabeth recorded the mass of her new baby every 7 days. ; The table below shows some of the values she recorded.;img;;a) Using a scale of 2 cm to represent 10 days, draw a horizontal axis for $$0 \leq -t \leq 70$$. ; Using a scale of 4 cm to represent 1 kg, draw a vertical m-axis for $$2 \leq m \leq 6$$. ; On your axes, plot the points given in the table and join them with a smooth curve.;;b) Use your graph to estimate;;b-i) The mass of the baby after 63 days,;;b-ii) When the baby;;b-iii) When the baby regain its birth mass.;;c-i) By drawing a tangent, find the gradient of the curve at (7, 3.10).;;c-ii) What does this gradient represent?;;d) Elizabeth wishes to estimate what the mass of the baby will be when it is 1 year old. ; She proposes to extend the graph line up to t = 365. ; Explain why it is not possible to estimate the baby in this way.Answers:

\end{document}
