\documentclass{article}
\begin{document}
ID: 199601002001
Content:
Apples cost 12 cents each. John has a $5 note and wishes to buy as many apples as possible. Calculate;;a) the number of apples that he can buy, [1];;b) the change that he will receive. [1]Answers:

ID: 199601002002
Content:
Calculate the exact value of;;a) $$69.2 \div 0.04$$, [1];;b) $$\sqrt[3]{8000}$$. [1]Answers:

ID: 199601002003
Content:
a) Find the smallest integer k such that $$4k\geq21$$. [1];;b) Find the largest integer n such that $$2n + 1 < 25$$. [1] Answers:

ID: 199601002004
Content:
Use the fact that $$372 \times 52 = 19344$$ to write down the exact value of;;a) $$3.72 \times 520$$, [1];;b) $$193.44 \div 0.52$$. [1]Answers:

ID: 199601002005
Content:
The population of Pakistan was recently estimated to be 102200000. Express 102200000 in standard form correct to 2 significant figures. [2]Answers:

ID: 199601002006
Content:
The temperature in Johns garden at noon was $$8^{\circ}C$$. At midnight the temperature was $$-6^{\circ}C$$. Both temperatures are given correct to the nearest degree.;;a) What is the largest possible value for the temperature at noon? [1];;b) Calculate the smallest possible value for the difference between the temperatures at noon and midnight? [2]Answers:

ID: 199601002007
Content:
Evaluate;;a) $$3^2 \times 2^3$$, [1];;b) $$7^0  \times 7^4 \div 7^{2} $$, [1];;c) $$(\frac{5}{4})^{-2}$$. [1]Answers:

ID: 199601002008
Content:
Given that $$f : x \mapsto \frac{2x - 7}{3}$$, find;;a) $$f(2)$$, [1];;b) an expression for $$f^{-1}$$. [2]Answers:

ID: 199601002009
Content:
Solve the simultaneous equations; 9x - 5y = 52; 4x -3y =27. [3]Answers:

ID: 199601002010
Content:
a) Express 75 km as a percentage of 5000 km. [1];;b) During a sale all prices in a shop were reduced by 5%. In the sale the price of a refrigerator was reduced by $9.70. Calculate the normal price of the refrigerator. [2]Answers:

ID: 199601002011
Content:
img;In the diagram, AB, CD and EF are parallel lines. XWV and XYZ are straight lines. The line XZ bisects angle BXW, and angle VWY = $$106^{\circ}$$.;;a) Calculate ;;a-i) $$W \hat VZ$$, [1];;a-ii) $$W \hat XY$$. [1];;b) Show that WXY is an isosceles triangle. [1]Answers:

ID: 199601002012
Content:
When it is 12 00 in London the time in Singapore is 20 00.;;a) What is the time in London when it is 12 30 in Singapore? [1];;b) A plane leaves Singapore at 12 30 to fly to London. The flight takes 13 hours 42 minutes. Calculate the time in London when it arrives. [2]Answers:

ID: 199601002013
Content:
$$\epsilon = {x: 1 \leq x \leq 30}$$, ; A = {x : x is a multiple 4}, ; B = {x : x is a multiple 3}, ;C = {x : x is a multiple 12}.;;a) List the elements of the set A. [1];;b) Find $$n(A \cap B)$$.;;c) Write down in set notation an equation involving the three sets A, B and C. [1]Answers:

ID: 199601002014
Content:
Factorize;;a) $$16 - 9x^2$$, [1];;b) $$6ab - 2ad - 3bc + cd$$. [2]Answers:

ID: 199601002015
Content:
img;In the diagram TA and TB are tangents to the circle ABC whose centre is O. TOC is a straight line.;;a) Give a reason why $$A \hat CT = B \hat CT$$. [1];;b) Given that $$A \hat TB = 72^{\circ}$$, calculate ;;b-i) $$A \hat OB$$, [1];;b-ii) $$C \hat AO$$. [1]Answers:

ID: 199601002016
Content:
img;ABC is a triangle in which AC = 13 cm, BC = 11 cm and AB = 20 cm. N is a point on BC produced, where CN = 5 cm and AN = 12 cm.;;a) Explain why $$A \hat NB$$ is a right angle. [1];;b) Expressing your answers as fractions, find ;;b-i) cos $$A \hat BN$$, [1];;b-ii) sin $$A \hat CB$$. [1]Answers:

ID: 199601002017
Content:
Solve the equations;;a) $$\frac{2}{x} = 5$$, [1];;b) $$4y^2 = 7y$$. [2]Answers:

ID: 199601002018
Content:
The times taken by an athlete to run 800 metres in three successive races were 2 minutes 0.8 seconds, 1 minute 59.1 seconds and 2 minutes 1.6 seconds.;;a) Calculate the average of these times. [2];;b) In order to qualify for an award of 8 minutes in 2400 metres, find the time taken of the final raceAnswers:

ID: 199601002019
Content:
A box of chocolates contained 6 chocolates with hard centres and 4 chocolates with soft centres. Ann took a chocolate, selected at random, from the box. Bruce then took a chocolate, selected at random, from the box. Expressing each answer as a fraction in its simplest form, find the probability that;;a) Ann took a chocolate with a hard centre, [1];;b) Ann took a chocolate with a hard centre and Bruce took a chocolate with a soft centre, [1];;c) both Ann and Bruce took a chocolate with a soft centre, [1];;d) Bruce took a chocolate with a soft centre. [1]Answers:

ID: 199601002020
Content:
img;The diagram is a map drawn to a scale of 1 cm to 5 km. The points A, B and C on the map represent three places A, B and C which are joined by straight roads. It is known that some treasure is buried at P, inside triangle ABC, where P is equidistant from CA and CB and 12 km from AB.;;a) By making appropriate constructions on the diagram indicate clearly the position of P, where the treasure is buried. [2];;b) Use the diagram to find;;b-i) the distance, in kilometers, from A to P, [1];;b-ii) the bearing of P from A. [1]Answers:

ID: 199601002021
Content:
A store sells large and small tins of both yellow and blue paint. The selling price of a large tin of either colour is $l and of a small tin of either colour is $s. The numbers of tins of each type that were sold one day are given in the following table. ;img; The total income from the sale of the yellow paint was $84 and from the blue paint was $104. It is given that A = $$\begin{bmatrix}5&3\\6&4\end{bmatrix}$$, B = $$\begin{bmatrix}l\\s\end{bmatrix}$$  and C = $$\begin{bmatrix}84\\104\end{bmatrix}$$.;;a) Write down an equation connecting A, B and C. [1];;b) Find $$A^{-1}$$. [2];;c) Calculate $$A^{-1} C$$. [1];;d) Explain the significance of your answer to part (c). [1]Answers:

ID: 199601002022
Content:
A bag contains 24 coins. Some of these are 10 cent coins and all of the others are 5 cent coins.;;a) If the number of 10 cent coins is x, write down an expression for the number of 5 cent coins. [1];;b) Write down an expression, in terms of x, for the total value, in cents, of the 24 coins. [1];;c) A second bag also contains 24 coins. In this bag the number of 5 cent coins is x and all of the others are 10 cent coins. The total value of the coins in the second bag is 30 cents more than the total value of the coins in the first bag. Use this information to form an equation in x and hence find x. [3]Answers:

ID: 199601002023
Content:
img;a) A translation maps $$\Delta  A$$ onto $$\Delta  B$$. Write down the column vector representing this translation. [1];;b) A rotation maps $$\Delta  A$$ onto $$\Delta  C$$. Write down the coordinates of the centre of this rotation. [2];;c) An enlargement maps $$\Delta  A$$ onto $$\Delta  D$$. Write down the coordinates of the centre of this enlargement and its scale factor. [2];;d) A shear maps $$\Delta  A$$ onto $$\Delta  E$$. Write down the shear factor. [1]Answers:

ID: 199601002024
Content:
To convert a recurring decimal into a fraction the following method may be used.;img;;a) Use the above method to covert the recurring decimal x = 0.292929;;b) Use a similar method to convert the recurring decimal 0.517517517Answers:

\end{document}
