\documentclass{article}
\begin{document}
ID: 199703002001
Content:
Find the value of;;a) $$2\frac{1}{2}+\frac{3}{5}$$ [1];;b) $$1.3\div 0.2$$ [1]Answers:

ID: 199703002002
Content:
a) Find, in its simplest form, the fraction which is exactly half-way between $$\frac{3}{4} and 1$$. [1];;b) Write down the value of this fraction as a decimal, giving your answer correct to one significant figure.  [1]Answers:

ID: 199703002003
Content:
The table gives the temperatures in Cambridge at 2 hourly intervals one day.;;a) Find the difference between the temperature at 1200 and 1800.  [1];;b) Between which two times did it get warmer?  [1]Answers:

ID: 199703002004
Content:
There are 30 students in a class. ; 22 study Mathematics, 16 study Science and 2 study neither Mathematics nor Science. By drawing a Venn diagram, or otherwise, find the number of students who study both Mathematics and Science. [2]Answers:

ID: 199703002005
Content:
img;Two plant pots are geometrically similar. ;The height of the smaller pot is 5 cm. ;The height of the larger pot is 15 cm.;;a) The diameter of the base of the larger pot is 7 cm. ;Find the diameter of the base of the smaller pot. [1];;b) Find the ratio of the volume of the smaller pot to that of the larger. ; Give your answer in the form 1: n. [1]Answers:

ID: 199703002006
Content:
a) Evaluate $$4^2+4^1+4^0$$ [1];;b) Write down the value of $$\sqrt{0.04}$$. [1];;c) Write down the following in order of size, starting with the smallest. ;$$\frac{1}{3}$$, $$0.3^{2}$$, 0.32 [1]Answers:

ID: 199703002007
Content:
img;a) Calculate the sum of the interior angles of a pentagon. [1];;b) A pentagon is shown in the answer space.;;b-i) Mark with an arc the interior angle that is reflex. [1];;b-ii) Measure the interior obtuse angle. [1]Answers:

ID: 199703002008
Content:
img;The bar chart shows the number of goals scored by a team in 19 matches. Find;;a) the mode of the distribution, [1];;b) the median of the distribution, [1];;c) the total number of goals scored. [1]Answers:

ID: 199703002009
Content:
Given that f(x) =$$\frac{2x+3}{5}$$, find;;a) f(6), [1];;b) $$f^{-1}$$(7). [2]Answers:

ID: 199703002010
Content:
X = $$(2, 1)$$, Y =$$\begin{bmatrix}3\\p\end{bmatrix}$$, Z =$$\begin{bmatrix}4&2\\-5&-2\end{bmatrix}$$. Find;;a) the value of p, given that XY = (2), [1];;b) the inverse of Z. [2]Answers:

ID: 199703002011
Content:
img;Which of the above could be the graph of;;a) y = $$\frac{1}{x}$$, [1];;b) y=1-x, [1];;c) y=$$x^2+1?$$ [1]Answers:

ID: 199703002012
Content:
Factorise;;a) $$2\pi r^2+2\pi rh$$, [1];;b) ac -3c + 2ab - 6b. [2]Answers:

ID: 199703002013
Content:
img;The bearing of B from A is $$072^{\circ}$$.;;a) Find the bearing of A from B. [1];;b) C is due South of B and BA = BC. Find the bearing of A from C. [2]Answers:

ID: 199703002014
Content:
a) Find the integer x such that $$x+1<7<x+3$$ [1];;b) Solve the inequality $$20-3y < y+4$$ [2]Answers:

ID: 199703002015
Content:
img;The unshaded region R in the diagram is defined by three inequalities of which one is $$y\leq 4-\frac{x}{2}$$.;;a) Write down the other two inequalities. [2];;b) Find the maximum value of x+3y, given that x and y satisfy these three inequalities. [1]Answers:

ID: 199703002016
Content:
img;In the diagram ACX is a straight line. ; AB = 12 cm, sin $$B \hat AC$$ = $$\frac{1}{2}$$ and sin $$B \hat CA$$= $$\frac{3}{4}$$.;;a) Write down the value of sin $$B \hat CX$$. [1];;b) Calculate BC. [3]Answers:

ID: 199703002017
Content:
img;On the grid in the answer space $$\vec{OA}$$ = a and $$\vec{OB}$$ = b. The point Y is also marked.;;a) On the grid mark clearly the point X, such that $$\vec{OX}$$ = 3b - 2a. ;;b) Write down $$\vec{OY}$$ in terms of a and b. [1];;c) It is given that $$\vec{OP}$$ = a + nb, where n takes all values from -3 to 3. On the grid draw the locus of P. [3]Answers:

ID: 199703002018
Content:
A book gives the following estimates of populations in the year 2000.;img;Assuming this information to be correct, find;;a) the total population of Africa and Asia, giving your answer in standard form,  [2];;b) the ratio of the population of Singapore to that of the World, expressing your answer in the form 1:n [2]Answers:

ID: 199703002019
Content:
Trains take 3 hours 42 minutes to travel between Aston and Barford.;;a) One train left Aston at 07 30. When did it arrive at Barford? [1];;b) On the return journey it reached Aston at 18 30. When did it leave Barford? [1];;c-i) Express the journey time (3 hours 42 minutes) in hours, giving your answer as a decimal. [1];;c-ii) The distance from Aston to Barford is 370 kilometres. ;Calculate the average speed of the train, giving your answer in kilometers per hour. [1]Answers:

ID: 199703002020
Content:
img;The diagram shows the speed-time graph for the first 20 seconds of a cyclist;;a) Calculate the distance travelled in the first 10 seconds. [1];;b) Calculate the total distance travelled in 20 seconds. [1];;c) On the axes in the answer space, draw the distance-time graph for this part of the journey. [2];img;Answers:

ID: 199703002021
Content:
Solve the equations.;;a) x(x+2)=0, [2];;b) y(y+2)=3. [3]Answers:

ID: 199703002022
Content:
img;The diagram shows a parallelogram ABCD. ;A is (1,6), B is (9,2), C is (9,0) and D is (1,4).;;a) Find the gradient of DC. [1];;b) Calculate the area of the parallelogram ABCD. [2];;c) The parallelogram is reflected in the line y = 2.; Find the coordinates of the image of the point D. [1];;d) Find the coordinates of the point about which ABCD has rotational symmetry of order 2. [1]Answers:

ID: 199703002023
Content:
img;The diagram shows a scale drawing of a plot of land ABCD with a house in one corner. It is drawn to a scale of 1 cm to 2m.;;a) On the diagram construct the locus of points which are;;a-i) equidistant from BA and BC,  [1];;a-ii) 4m from the house. [3];;b) A tree is to be planted nearer to BC than BA and at least 4 m from the house. On the diagram shade the region representing the area in which the tree could be planted. [1]Answers:

ID: 199703002024
Content:
img;a) By considering the number patterns, complete lines (1), (2) and (3) in the table.;$$3^4-16=1 \times 5 \times (3^2+4)$$;$$4^4-16=2 \times 6 \times (4^2+4)$$;$$5^4-16=3 \times 7 \times (5^2+4)$$;;b) Use your answer to part (3) and the information given below to find the three prime factors of 50609.[$$15^2=225, 15^4= 50625.$$][2]Answers:

\end{document}
