\documentclass{article}
\begin{document}
ID: 199801002001
Content:
a) Calculate the exact value of $$21.08 \div 8$$. [1];;b) Find 8% of 65 cm. [1]Answers:

ID: 199801002002
Content:
Find the value of;;a) $$\frac{2}{3}-\frac{4}{7}$$, [1];;b) $$\frac{3}{5}\div \frac{3}{4}$$. [1]Answers:

ID: 199801002003
Content:
Solve the quadratic equation (x + 3)(2x - 1) = 0. [2]Answers:

ID: 199801002004
Content:
img;The diagram shows a regular hexagon inscribed in a circle. Shade two segments of the circle so that the shaded diagram has rotational symmetry of order 2. [2]Answers:

ID: 199801002005
Content:
Evaluate;;a) $$(\frac{3}{10})^2$$, [1];;b) $$5^{-2}$$. [1]Answers:

ID: 199801002006
Content:
a) Express 63 as the product of its prime factors. [1];;b) What is the smallest positive integer value of n for which 63n is a multiple of 35? [1]Answers:

ID: 199801002007
Content:
One day, the high tide was 2.3 m above and the low tide 2.0 m below a mark on a harbor wall. Both measurements are correct to one decimal place. Calculate, in metres, a lower bound for the difference between the high and low tides. [2]Answers:

ID: 199801002008
Content:
a) Calculate the exact value of $$\sqrt[3]{8 \times 10^6}$$. [1];;b) The population of Nigeria was recently estimated to be 103940000. Express 103940000 in standard form, correct to 3 significant figures. [2];Answers:

ID: 199801002009
Content:
img;In the diagram, O is the centre of the circle ABCD. The straight lines AC and BD intersect at O. The tangent at A meets CD produced at E and $$A \hat ED=32^{\circ}$$. Calculate;;a) $$A \hat BD$$, [2];;b) $$A \hat OD$$. [1]Answers:

ID: 199801002010
Content:
img;A petrol station sells 4-star, unleaded and diesel fuel. The pie chart represents the amounts of these fuels sold during one week. The total amount of fuel sold during this week was 24000 litres.;;a) How many litres of 4-star petrol were sold? [1];;b) If 6800 litres of diesel were sold, calculate the value of x. [2]Answers:

ID: 199801002011
Content:
Given that  $$f:x->\frac{3x-5}{2}$$, find;;a) $$f(3\frac{1}{3})$$, [1];;b) an expression for $$f^{-1}$$. [2]Answers:

ID: 199801002012
Content:
img;On the grid, $$\vec{OP}=p$$ and $$\vec{OQ}=q$$.;;a) Mark clearly on the grid the point X such that $$\vec{OX}=2p$$ and the point Y such that $$\vec{OY}=2p-3q$$. [2];;b) What is the special name given to the quadrilateral OQXY? [1];;Answers:

ID: 199801002013
Content:
img;img;The number line above shows the set P of real numbers x, where $$P={x:x \geq 4}$$. The number line above shows the set Q of real numbers x, where $$Q={x:2\leq x<5}$$. On the number lines given, illustrate the following sets of real numbers x.;;a);img;$$A={x:x\leq3}$$ [1];;b);img;$$B={x:-2<x<6}$$ [1];;c);img;$$A \cap B$$ [1]Answers:

ID: 199801002014
Content:
a) A piece of string of length 160 cm is divided into two parts in the ratio 1 : 9. Calculate the length of the smaller part. [1];;b) When a dealer sold a car for $14300, he made a profit of 10%. Calculate how much the dealer paid for the car. [2]Answers:

ID: 199801002015
Content:
Express as a fraction in its simplest form $$\frac{4}{x+3}+\frac{3}{x}$$. [3]Answers:

ID: 199801002016
Content:
A business makes toy buses and toy lorries. The following table is used in calculating the cost of manufacturing each toy.;img; Labour costs $8 per hour, wood costs $1 per block and paint costs $2 per tin. ; It is given that $$A=\begin{bmatrix}6&4&3\\3&4&2\end{bmatrix}$$, $$B=\begin{bmatrix}8\\1\\2\end{bmatrix}$$ and C = AB.;;a-i) Evaluate C. [1];;a-ii) Explain what the numbers in your answer represent. [1];;b) In addition, D = (100 200).;;b-i) Evaluate DC. [1];;b-ii) Explain what your answer represents. [1]Answers:

ID: 199801002017
Content:
img;The diagram, which shows the sector AOB of a circle, represents a piece of card. The radius of the sector is 24 cm and the angle AOB is $$120^{\circ}$$.;;a) Calculate, as a multiple of $$\pi$$, the length of the arc AB. [2];;b) The card is used to make a hollow cone by joining the edges OA and OB. Calculate the radius of the base of the cone. [2]Answers:

ID: 199801002018
Content:
One milligram, 1 mg, is one thousandth of a gram. One microgram, 1 $$\mu g, is one millionth of a gram$$;;a) Express 3 mg in grams, as a decimal. [1];;b) How many micrograms are equivalent to 1 mg? [1];;c) Every 100 g of a certain cereal contains 300 $$\mu g$$ of Frolic Acid. What fraction of cereal is Frolic Acid?Answers:

ID: 199801002019
Content:
img;The diagram is the speed-time graph of a journey.;;a) Calculate;;a-i) the retardation during the last 20 seconds of the journey, [1];;a-ii) the total distance travelled in the 80 seconds. [2];;b) The distance-time graph for $$40\leq t\leq 60$$ is a straight line. State the gradient of this line. [1]Answers:

ID: 199801002020
Content:
img;img;ABC is a triangle with AB = 5 cm, BC = 4 cm and angle ABC = $$120^{\circ}$$. AB is produced to D and angle BCD = $$90^{\circ}$$. Using as much information given in the table below as is necessary, calculate;;a) the area of triangle ABC, [2];;b) the length of BD. [3]Answers:

ID: 199801002021
Content:
It is given that $$h=\frac{3u^2}{8g}$$.;;a) Calculate an estimate of h when u = 40.97 and g = 9.81. [3];;b) Express u in terms of h and g. [2]Answers:

ID: 199801002022
Content:
a) Solve the equation 7x - 4(x - 3) = 27. [2];;b) Simplify and factorize $$y(2-y)(3-y)+y^2(y+5)$$. [3]Answers:

ID: 199801002023
Content:
On a certain stretch of road, the speeds of 100 cars were recorded. The results are summarized in the table below.;img;;a);img;On the grid, draw a frequency polygon to show this information. [2];;b) Calculate an estimate of the mean speed of these cars. [3]Answers:

ID: 199801002024
Content:
img;In the diagram, the points A, B and C have coordinates (0, 1), (1, 3) and (-1, -1).;;a) Calculate the gradient of the line AB. [1];;b) Find the equation of the line AB. [1];;c) The point (10, k) lies on the line AB produced. Find the value of k. [1];;d) The length of the line segment AB is $$\sqrt{l}$$. Calculate the value of l. [1];;e) The triangle BCD has line of symmetry y = x. Write down the coordinates of D. [2]Answers:

\end{document}
