\documentclass{article}
\begin{document}
ID: 200004002001
Content:
In 1997 a salesman was paid a basic salary of $33000.;;a) He was paid in 12 equal monthly installments. Calculate his salary each month [1];;b) At the end of the year he was also paid a bonus of $$1 \frac{1}{2}$$% of the value of the sales that he had made during the year. In 1997 the value of his sales was $196000. Calculate the total income (basic salary plus bonus) that he received in 1997. [2];;c) In 1998 his basic salary was increased to $36000.;;c-i) Calculate the percentage increase in his basic salary from 1997 to 1998. [2];;c-ii) In 1998 he was again paid a bonus of $$1 \frac{1}{2}$$% of the value of his sales. His total income was $39660. Calculate the value of the sales that he made that year. [2];;d) In 1999 his basic salary was unchanged at $36000, but he percentage used to calculate his bonus was changed. The value of his sales was $284000 and his total income was $42390. Calculate the percentage used to find his bonus in 1999. [2];;e) His basic salary of $33000 in 1997 was an increase of 10% on his basic salary in 1996. Calculate his salary in 1996.Answers:

ID: 200004002002
Content:
a) The numbers (x-1), x and (x+1) are three successive positive integers. When they are multiplied together, the product of the three numbers is 120 times their sum.;;a-i) Use this information to form an equation, in terms of x, and show that it simplifies to $$x^3 - 361x = 0$$ [2];;a-ii) Factorise completely $$x^3 - 361x = 0$$. [2];;a-iii) Find the three integers. [2];;b) Make k the subject of the formula $$c = \frac{k^2 + h^2}{h}$$ [3]Answers:

ID: 200004002003
Content:
img;In the diagram, AC = 8cm, CE = 4cm and the area of triangle EBC = $$4.2cm^2$$.;;a) Calculate the area of triangle ABC. [1];;b) An enlargement, with centre A, maps triangle ABC onto triangle ADE. Calculate the scale factor of the enlargement. [1];;c) Another enlargement, with centre E, maps triangle EBC onto triangle EFA. BC = 3.6cm. Calculate;;c-i) the length of AF, [1];;c-ii) the area of triangle EFA, [2];;c-iii) the area of triangle BAF. [2]Answers:

ID: 200004002004
Content:
img;In the diagram, AC is a diameter of the circle ABCD. The straight lines EBA and ECD cut the circle at A, B, C and D. AC and BD cut at F. Angle BAC = $$42^{\circ}$$ and angle DAC = $$31^{\circ}$$. Calculate;;a) angle BCD, [1];;b) angle ACD, [2];;c) angle ABF, [1];;d) angle AFB, [1];;e) angle AED. [1]Answers:

ID: 200004002005
Content:
img;The diagram shows four towns, A, B, C and D. C is 110 km due East of A. $$A \hat BC = 90^{\circ}$$ and AB = 70 km.;;a) Calculate;;a-i) the distance BC, [2];;a-ii) the bearing of B from A. [3];;b) Given that D is due South of C and that $$C \hat AD = 28^{\circ}$$, calculate the distance CD. [2];;c) An aircraft flies from A to B, then from B to C, then from C to D and finally from D to A. Calculate the total distance that it flies. [3]Answers:

ID: 200004002006
Content:
Answer the whole of this question on a sheet of plain paper.;;a) Draw a quadrilateral ABCD in which the base AB = 10 cm, $$B \hat AD = 82^{\circ}$$,  AD = 7.2 cm, $$A \hat BC = 105^{\circ}$$ and $$A \hat DC = 75^{\circ}$$. Measure and write down the length of AC. [3];;b) On your diagram, draw the locus of all the points within the quadrilateral which are;;b-i) equidistant from A and B,;;b-ii) equidistant from A and D. [2];;c) Mark the point E where these two lines meet. Measure and write down the length of AE. [1];;d) On your diagram, draw the locus of all points whose distance from E is equal to AE. [2];;e) A point P lies within the quadrilateral and is such that ;P is nearer to B than A and;P is nearer to D than A.;On your diagram, shade the region of the quadrilateral in which P must lie. [1]Answers:

ID: 200004002007
Content:
img;[The value of $$\pi$$ is 3.142 correct to three decimal places.];Diagram I shows an open rectangular box of height 15 cm.;The box contains 10 cylindrical tins.;The tins touch one another and the sides of the box.;Each tin has radius 6 cm and height 15 cm.;;a-i) Each tin has a label wrapped round it, which exactly covers its vertical surface. Calculate the area of paper needed for one label. [2];;a-ii) Calculate the volume of one tin. [2];;b) Diagram II shows the view of the box and the tins from above.;PQRS is the rectangular cross-section of the box.;The points A, B and C are the centres of the circular tops of three adjacent tins which touch one another. The midpoint of AB is N.;;b-i) Write down the length of AC. [1];;b-ii) Calculate;;b-ii-a) the length of CN, [2];;b-ii-b) the length of PS. [2];;c) The height of the box is also 15 cm. Calculate the volume of the space in the box which is not occupied by the tins. [3]Answers:

ID: 200004002008
Content:
img;The diagram shows two horizontal triangular fields, ABC and ACD, which are surrounded by hedges.;It is given that DAB is a straight line, AC = 65 m, $$C \hat AB = 60^{\circ}$$ and $$A \hat BC = 72^{\circ}$$.;;a) Calculate the length of the hedge BC. [2];;b) The hedge AD has length 84 m. Calculate;;b-i) the area of $$\Delta ACD$$. Calculate;;b-ii) the length of the hedge CD. [4];;c) A vertical tree is growing at C. The angle of elevation of the top of the tree from A is $$14^{\circ}$$.;;c-i) Calculate the height of the tree. [2];;c-ii) A boy has climbed exactly half way up the tree. Calculate the angle of depression of D when viewed by the boy. [2]Answers:

ID: 200004002009
Content:
Answer the whole of this question on a sheet of graph paper.;The table below gives some values of x and the corresponding values of y, correct to two decimal places, where;img;;a-i) Find the value of p and the value of q. [1];;a-ii) Using a scale of 2 cm to 1 unit, draw a horizontal x-axis for $$-1 \leq x \leq 4$$. ;Using a scale of 1 cm to 1 unit, draw a vertical y-axis for $$-2 \leq y \leq 14$$. ;On your axes, plot the points given in the table and join them with a smooth curve. [3];;a-iii) Using your graph, find the values of x for which y = 3. [2];;b) By drawing a tangent, find the gradient of the curve at the point where x = 3. [2];;c) On the axes used in part (1), draw the graph of y = 10 - x for values of x in the range $$-1 \leq x \leq 4$$. [2];;d) Write down, and simplify, the cubic equation which is satisfied by the values of x at the points where the two graphs intersect. [2]Answers:

ID: 200004002010
Content:
Answer the whole of this question on a sheet of graph paper.;One day a farmer collected 340 eggs from his chickens.;The table below shows the distribution of the masses of the eggs.;img;;a) When a histogram is drawn to illustrate this information, the rectangle representing the eggs with masses in the interval $$42 < m \leq 46$$ has width 2 cm and height 3 cm.;Find the width and the height of the rectangle representing the eggs with masses in the interval $$46 < m \leq 48$$ [2];;b) Copy and complete the cumulative frequency table below. [1];img;;c) Using a scale of 2 cm to represent 5 grams, draw a horizontal m-axis for $$30 \leq m \leq 70$$. Using a scale of 2 cm to represent 50 eggs, draw a vertical axis for values from 0 to 340. On your axes, draw a smooth cumulative frequency curve to illustrate this information. [3];;d) Use your graph to find;;d-i) the median mass of the eggs, [1];;d-ii) the interquartile range. [2];;e) The farmer classifies 60 of the eggs to be ;;e-i) Use yAnswers:

ID: 200004002011
Content:
The distance between two towns, A and B, is 100 km. Mr Jones drove from A to B at an average speed of v km/h.;;a) Write down an expression, in terms of v, for the time, in hours, that he took to complete the journey from A to B. [1];;b) On the return journey, his average speed was 6 km/h greater than his speed from A to B.;;Write down an expression, in terms of v, for;;b-i) his speed for the journey from B to A, [1];;b-ii) the time, in hours, that he took for the journey from B to A. [1];;c) Given also that the return journey took 20 minutes less than the journey from A to B, form an equation in v, and show that it reduces to $$v^2 + 6v - 1800 = 0$$ [3];;d) Solve the equation $$v^2 + 6v - 1800 = 0$$, giving both answers correct to three significant figures. [4];;e) Calculate, correct to the nearest minute, the total time that Mr Jones spent travelling. [2]Answers:

\end{document}
