\documentclass{article}
\begin{document}
ID: 200003002001
Content:
Find the value of ;;a) $$28 \div 3 \frac{1}{2}$$, [1];;b) $$0.3 \times 0.02$$. [1]Answers:

ID: 200003002002
Content:
a) Express $$\frac{13}{40}$$ as a decimal. [1];;b) A rope is cut into two pieces in the ratio 3 : 2. The longer piece is 9.6m long. Find the length of the shorter piece. [1]Answers:

ID: 200003002003
Content:
img;A rectangular block of wood has dimensions 24 cm by 9 cm by 7 cm. It is cut up into children of dimensions 3cm by 3cm by 3cm;;a) Find the largest number of bricks that can be cut from the block. [1];;b) Find the volume of wood that is left. [1]Answers:

ID: 200003002004
Content:
a) Calculate $$\frac{5}{8}$$ of $14.00. [1];;b) Express the ratio 400 metres to 3 kilometres in its simplest form. [1]Answers:

ID: 200003002005
Content:
img;The diagram is taken from an advertisement of a car manufacturer. It claims to show that the number of cars produced has doubled between 1990 and 1999. Explain briefly why the advertisement might be considered misleading. [2]Answers:

ID: 200003002006
Content:
a) Kim pays a bill for $52.45 with a $100 note. How much change should she receive? [1];;b) Ali invests $2500 at an annual rate of 6% simple interest. After 8 months he withdraws all the money. How much does he receive? [2]Answers:

ID: 200003002007
Content:
img;In the diagram, ABC is a triangle in which AC= BC. The point D is on AC produced and DE is parallel to CB. Given that $$B \hat CD = 108^{\circ}$$, calculate;;a) x, [1];;b) y, [1];;c) z. [1]Answers:

ID: 200003002008
Content:
a) Express 0.068 as a percentage. [1];;b) A painting was bought for $12 and sold some years later for $138. Calculate the percentage profit. [1]Answers:

ID: 200003002009
Content:
a) Write down, correct to the nearest integer, the value of $$\sqrt{896}$$[1];;b) In 1998 there were $$4.9 \times 10^7$$ people living in England and of these $$9.3 \times 10^6$$ were under 16 years of age. Find the number of people who were 16 or over. Give your answer in standard form. [2]Answers:

ID: 200003002010
Content:
p = $$\begin{bmatrix}1\\-4\end{bmatrix}$$, q = $$\begin{bmatrix}-3\\4\end{bmatrix}$$ and r = $$\begin{bmatrix}m\\2\end{bmatrix}$$;;a) Find |q|. [1];;b) Express 2p - q as a column vector. [1];;c) Given that p is parallel to r, find m.Answers:

ID: 200003002011
Content:
a);img;Are triangles ABC and DEF similar? Explain your answer clearly [1];;b);img;Triangles LMN and PQR are similar. Calculate the value of x. [2]Answers:

ID: 200003002012
Content:
A is the point (-1, 0) and B is the point (2, 6). Find;;a) the coordinates of the midpoint of AB, [1];;b) the gradient of the line AB, [1];;c) the equation of the line parallel to AB, through the point (0, 4). [1]Answers:

ID: 200003002013
Content:
img;[The value of $$\pi$$ is 3.14 correct to three significant figures.] In the diagram, the circle, centre O, passes through A and B. The radius of the circle is 4 cm and $$A \hat OB = 45^{\circ}$$.;;a) Find the area of the minor sector AOB. [2];;b) The tangent at A meets OB produced at T. Find the shaded area. [1]Answers:

ID: 200003002014
Content:
a) Express 0.052 square metres in square centimeters. [1];;b-i) Express 90 as the product of its prime factors. [1];;b-ii) The lowest common multiple of 6, 15 and x is 90 Find the two possible values of x which are odd numbers. [1]Answers:

ID: 200003002015
Content:
img;In the diagram, ABC is a straight line, $$C \hat BD = 68.2^{\circ}, B \hat CD = 90^{\circ},$$ CD = 5 cm and AD = 8cm. Using as much of the information given in the table below as is necessary, find;;a) sin x, giving your answer as a fraction, [1];;b) cos y, [1];;c) BC. [1]Answers:

ID: 200003002016
Content:
img;The diagram is the speed-time graph of the first 30 seconds of a journey. Find;;a) the speed when t = 18, [1];;b) the acceleration during the first 10 seconds, [1];;c) the total distance travelled in the 30 seconds. [2]Answers:

ID: 200003002017
Content:
img;In the diagram, ABCD is a quadrilateral with BA parallel to CD. AC and BD meet at X where CX = 8 cm and XA = 10 cm.;;a) Given that BD = 27 cm, find the length BX. [2];;b) Find the ratio area of triangle BXC : area of triangle AXD. [2]Answers:

ID: 200003002018
Content:
img;The diagram represents the circular cross-section of a road tunnel. AB represents the horizontal surface of the road. M is the midpoint of AB and is vertically below N, the top of the circle. AB = 8 m and MN = 10 m. The circle has centre O and radius r metres.;;a) Express OM in terms of r. [1];;b) Form an equation in r and solve it to find the radius of the tunnel. [2]Answers:

ID: 200003002019
Content:
A bag contains 3 black and 2 white balls. Two balls are taken from the bag at random, without replacement. By drawing a tree diagram, or otherwise, calculate the probability that ;;a) Both balls are black, [1];;b) At least one ball is white, [1];;c) The two balls are the same colour. [2]Answers:

ID: 200003002020
Content:
Some children were asked how many television programme they had watched on the previous day. The table shown the result.;img;;a) Write down the largest possible value of x given that the mode is 1. [1];;b) Write down the largest possible value of x given that the median is 1. [1];;c) Calculate the value of x given that the mean is 1. [2]Answers:

ID: 200003002021
Content:
You are asked to investigate the price that a shop should charge for a particular toy. When the toy is priced at $x, the shop sells (90 - 100x) toys.;;a) Write down an expression, in terms of x, for the total amount, in dollars, received by the shop for the sale of these toys. [1];;b) Find the value of x if the amount received is to be as large as possible. You should use the grid and/or the table to help you in your investigation. Marks will be awarded for clear working. [3];img;Answers:

ID: 200003002022
Content:
a) Factorise $$3c(d - 2e) - (d - 2e)$$. [1];;b) Solve the inequality 4k - 1 < 14 + k. [1];;c) Solve the simultaneous equations ;$$y = 6x - 4$$ ;$$3x - 2y = 5$$. [3]Answers:

ID: 200003002023
Content:
img;The graph shows the charges made by two companies for telephone calls lasting up to 10 minutes. Kingcom charges 40 cents for calls of 3 minutes or less and then at the constant rate of 10 cents per minutes. Phoneshop charges a connection fee of p cents and all calls are charge at the constant rate of q cents per minute. Using these graphs, or otherwise, find;;a) The cost of a 7 minute call using Kingcom, [1];;b) The value of p, [1];;c) The value of q, [1];;d) The range of times for which it would be cheaper to use Kingcom. [2]Answers:

ID: 200003002024
Content:
img;The diagram below shows three triangles, A, B and C.;;a) Describe fully the single transformation which maps triangle a onto;;a-i) Triangle B, [2];;a-ii) Triangle C. [2];;b) Triangle A is mapped onto triangle D by an enlargement with centre (1, 0) and scale factor -2. Draw triangle D on the diagram.Answers:

\end{document}
