\documentclass{article}
\begin{document}
ID: 200001002001
Content:
a) Write down the remainder when 365 is divided by 7. [1];;b) There were 365 days in the year 1993. The first day of the year was a Friday. On what day of the week did 1994 begin? [1]Answers:

ID: 200001002002
Content:
The price of a box of soap powder increased from $2.50 to $2.65. Calculate the percentage increase in the price. [2]Answers:

ID: 200001002003
Content:
A is the point (7, 3) and B is the point (5, 11). Find;;a) the coordinates of the midpoint of AB, [1];;b) the vector $$\vec{AB}$$. [1]Answers:

ID: 200001002004
Content:
The rate of exchange between Swedish krona (K) and British pounds (P) was 12.90K = 1P. Calculate;;a) the number of krona received in exchange for 50P. [1];;b) the number of pounds received in exchange for 12900K. [1]Answers:

ID: 200001002005
Content:
img;The flag A is mapped onto the flag B by a clockwise rotation of $$z^{\circ}$$ about the centre P. Write down;;a) the value of z, [1];;b) the coordinates of P. [1]Answers:

ID: 200001002006
Content:
Given that $$f:x->2x+1$$, find an expression for $$f^{-1}$$. [2]Answers:

ID: 200001002007
Content:
a);img;On the Venn diagram, shade the set $$(A\cap B)\cup C$$. [1];;b) The Universal set is the set of all positive integers and P={x:x < 10}. Complete the statement. [1]Answers:

ID: 200001002008
Content:
img;The diagram shows two straight lines, AB and CD, which are unequal in length and bisect each other at O. Explain why the triangles AOC and BOD are equal in area. [2]Answers:

ID: 200001002009
Content:
img;A vertical post of height 1.5 m and a vertical flagpole of height 7.5 m stand on horizontal ground.;;a) Express the height of the post as a percentage of the height of the flagpole. [1];;b) At a certain time of day, the flagpole casts a shadow of length 6 m. Calculate the length of the shadow cast by the post. [2]Answers:

ID: 200001002010
Content:
img;AB, BC and CD are adjacent sides of a regular polygon. Given that $$C \hat AB=18^{\circ}$$, calculate;;a) an exterior angle of the polygon, [1];;b) the number of sides of the polygon, [1];;c) $$A \hat CD$$. [1]Answers:

ID: 200001002011
Content:
The matrix $$A=\begin{bmatrix}1&x\\-1&2\end{bmatrix}$$.;;a) Write down an expression, in terms of x, for the determinant of A. [1];;b) Given that the determinant of A is 5,;;b-i) calculate the value of x, [1];;b-ii) Write down $$A^{-1}$$. [1]Answers:

ID: 200001002012
Content:
Express as a single fraction $$\frac{2}{x+2}-\frac{x}{x+3}$$. [3]Answers:

ID: 200001002013
Content:
a) Express 6700 in standard form. [1];;b) $$3 \times 10^{3} +2 \times 10^{1} +4 \times 10^{x}+5 \times 10^{y}=3024.05$$, where x and y are integers. Write down the value of x and the value of y. [2]Answers:

ID: 200001002014
Content:
Solve the simultaneous equations 5x + 4y = 0, 4x + 5y = -18. [3]Answers:

ID: 200001002015
Content:
a) Solve the inequality 4 - x < 6. [1];;b) In the diagram below, the unshaded region R is defined by three inequalities, one of which is $$x \geq 0$$.;img;Write down the other two inequalities. [2]Answers:

ID: 200001002016
Content:
Three brands of cat food are sold at two stores. The following tables show the price of each brand at each store.;img;The prices are given in cents per 100 g. Data is given for the months May and June. It is given that $$X=\begin{bmatrix}9.4&9.6\\10.2&10.4\\11.4&11.0\end{bmatrix}$$ and $$Y=\begin{bmatrix}9.8&10.0\\10.2&10.2\\12.0&12.0\end{bmatrix}$$.;;a-i) Evaluate Y - X. [1];;a-ii) Explain what the numbers in your answer represent. [1];;The cat food is sold in tins containing 500 g. Write down the matrix M such that the product XM will show, for each brand, the total cost, in cents, of buying ten tins at both stores during May. [2]Answers:

ID: 200001002017
Content:
img;The probability that Catherine oversleeps is 0.4. If she oversleeps, the probability that she cycles to school is 0.7. If she does not oversleep, the probability that she cycles to school is 0.1. ;;a) Complete the tree diagram to represent this information. [2];;b) Calculate the probability that Catherine cycles to school. [2]Answers:

ID: 200001002018
Content:
a) Factorize completely $$3p^{2} -12$$. [2];;b) Solve the equation $$x^{2} +2x-3=0$$. [2]Answers:

ID: 200001002019
Content:
160 candidates took an examination. The mark distribution produced the following information: the median mark was 39, the inter-quartile range was 23 marks, the lower quartile was 27 marks, the highest mark scored was 68, the lowest mark scored was 6.;;a) Calculate the upper quartile of this distribution. [1];;b) On the axes shown draw the cumulative frequency curve to represent this information. [3];img;Answers:

ID: 200001002020
Content:
img;The diagrams above are the speed-time and the distance-time graphs of the same journey.;;a) Calculate;;a-i) the acceleration during the first 20 seconds, [1];;a-ii) the value of k. [2];;b) During the last part of the journey, the retardation is $$3m/s^{2} $$. Calculate the time taken while slowing down. [1]Answers:

ID: 200001002021
Content:
img;The diagonal AC of a square ABCD is drawn.;;a) Construct accurately;;a-i) the square ABCD, [1];;a-ii) the isosceles triangle ABE, with AE = BE = 6.5 cm, and E outside the square. [2];;b) Measure CE. [1]Answers:

ID: 200001002022
Content:
Given that $$c=\frac{2d+1}{3d-1}$$,;;a) calculate the value of c when $$d=\frac{1}{4}$$, [1];;b) express d in terms of c. [3]Answers:

ID: 200001002023
Content:
a);img;ABC is an equilateral triangle of side 2 units. AN is perpendicular to BC. Show that $$cos 60^{\circ}=\frac{1}{2}$$. [1];;b);img;In the diagram, which is not accurate: RRAnswers:

ID: 200001002024
Content:
An examination was taken by 160 pupils. The frequency distribution of the marks out of 100 is shown in the table below:;img;;a) Complete the cumulative frequency table for this distribution. [1];img;;b) A pie chart is drawn to represent this information.;img;Calculate the angle of the sector representing the number of pupils scoring more than 70 marks. [2];;c) A histogram is drawn to represent this information. Complete the histogram. [2]Answers:

ID: 200001002025
Content:
img;The diagram shows a sequence of right-angled triangles, $$ABR_1$$, $$ABR_2$$, $$ABR_3$$ ..., all with height AB = 1.;;a) In the first triangle, BR1 = 1. Given that $$AR_1=\sqrt{x}$$, show that x = 2. [1];;b) In the second triangle, $$BR_2=AR_1$$. Show that $$AR_2=\sqrt{3}$$. [1];;c) The sequence continues with $$BR_3=AR_2$$, $$BR_4=AR_3$$, and so on.;;c-i) Show that $$R_1$$ is the midpoint of $$BR_4$$. [2];;c-ii) Find the sides of the 10th triangle, $$ABR_{10}$$. [1];;c-iii) Write down, in terms of n, the sides of the nth triangle, $$ABR_{n}$$. [1]Answers:

\end{document}
