\documentclass{article}
\begin{document}
ID: 200102002001
Content:
a) A survey of a TV Channel showed that there were 50 minutes of advertisements during a 5 hour period. Calculate, in the form 1 : n, the ratio of the time spent on	advertisements to the total time. [1];;b) A film started at 23 40 and finished $$1\frac{3}{4}$$ hours later. At what time did the film finish? [1];;c) Sam wants a television. He can either buy or rent it. ;;c-i) The cost of buying it is $960. Sam would pay a deposit of 30% followed by 12 equal monthly payments.;;c-i-a) Calculate the deposit. [1];;c-i-b) Calculate each monthly payment. [2];;c-ii) The cost of renting the television is $310 for the first year and then $20 for each month after the first year.;;c-ii-a) Calculate the total cost of renting it for 3 years. [1];;c-ii-b) When will it become more expensive to rent the television than to buy it for $960? [2];;;c-iii) In a sale, a television is reduced from $960 to $900. Calculate the percentage discount. [2]Answers:

ID: 200102002002
Content:
a) Alice, Ben and Chris shared some money. Alice received $x. Ben received twice as much as Alice. Chris received $31 more than Alice.;;a-i) Write down, and simplify, an expression in terms of x, for the total number of dollars they shared. [2];;a-ii) Given that $115 was shared, form an equation in x, and hence find the amount received by Chris. [2];;b) Remove the brackets and simplify (3t - 2) (5 - 2t). [2];;c) Solve the equation $$y^{2} +7y+3=0$$, giving both answers correct to two decimal places. [4]Answers:

ID: 200102002003
Content:
img;The diagram shows footpaths BR and CR in a park ABCDR. BR = 140 m, CR = 120 m and AB = 82 m. $$B \hat CR=48^{\circ}$$, $$D \hat CR=59^{\circ}$$ and $$A \hat BR=C \hat DR=90^{\circ}$$. Calculate;;a) CD, [2];;b) $$A \hat RB$$, [2];;c) $$C \hat BR$$. [3]Answers:

ID: 200102002004
Content:
$$\epsilon$$ = {1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11} ; A = {x : x is an even number} ; B = {x : x is a multiple of 3};;a) Draw a Venn Diagram to illustrate these sets, indicating the numbers of each subset. [2];;b-i) A number n is chosen at random from $$\epsilon$$. Find the probability that;;b-i-a) $$n in A$$, [1];;b-i-b) $$n in A'$$ , [1];;b-i-c) $$n in A \cap B$$, [1];;b-i-d) $$n = 14$$;;b-ii) A second number m is chosen at random from the complete set $$\epsilon$$. Find the probability that the sum of n and m is 18. [2]Answers:

ID: 200102002005
Content:
a);img;In the diagram, A, B, C, D and E lie on the circumference of a circle centre O. OB is parallel to DC. AD is a diameter of the circle. $$A \hat OB=38^{\circ}$$. Find;;a-i) $$O \hat AB$$, [1];;a-ii) $$O \hat DC$$, [1];;a-iii) $$B \hat CD$$, [1];;a-iv) $$A \hat EB$$, [1];;a-v) $$B \hat ED$$. [1];;b);img;[The value of $$\pi$$ is 3.142, correct to 3 decimal places.] ; In the diagram, the shaded region is a large circle with a small circle cut out of it. The large circle has radius 30 cm and centre H. HK is a diameter of the small circle. Calculate;;b-i) the area of the shaded region, [2];;b-ii) the perimeter of the shaded region. [2]Answers:

ID: 200102002006
Content:
Mary uses some straws to make shapes which are squares with the corners missing. The straws are joined together by three different types of connector - ; The diagram below shows the first four shapes she makes.;img;; The table below shows the numbers of different types of connector used.;img;img;;a) Copy the table and complete the columns for Shapes 3 and 4. [2];;b) By studying the number patterns in your table, complete the column for Shape 5. [1];;c) Find, in terms of n, expressions for;;c-i) E, [1];;c-ii) M, [1];;c-iii) the total number of connectors needed for Shape n. [1];;d) Find the total number of connectors needed for Shape 50. [2]Answers:

ID: 200102002007
Content:
img;[The value of $$\pi$$ is 3.142, correct to three decimal places.] ; [The volume of a sphere is $$\frac{4}{3}\pi r^{3} $$.] ; Sarah makes biscuits. The amount of mixture required to make one biscuit is $$18cm^{3} $$. Before it is cooked, the mixture is rolled into a sphere.;;a) Calculate the radius of the sphere. [2];;b-i) After it is cooked, the biscuit becomes a cylinder of radius 3 cm and height 0.7 cm. The increase in volume is due to air being trapped in the biscuit. ; Calculate the volume of air contained in a biscuit. [2];;b-ii) Express this volume of air as a percentage of the total volume of the mixture. [2];;c-i);img;The biscuits are packed in a box. The cross-section of the box is a regular hexagon, containing 7 biscuits, arranged as shown in Diagram I.;;Three of the biscuits are shown in Diagram II. O is the centre of the hexagon and of the middle biscuit. B is the point where two biscuits touch. A and C are the centres of these biscuits. E is the midpoint of the side DF of the. Estimate the value of DF Answers:

ID: 200102002008
Content:
img;Answer the whole of this question on a sheet of graph paper. ; The diagram shows a sketch of the curve $$y=36-x^{2} $$. The curve crosses the axes at H, K and L. O is the origin.;;a) Show that the area of triangle OHK is 108 square units. [2];;b) The point P lies on the curve between H and K. The coordinates of P are (x, y). PQRS is a rectangle with Q on the curve and R and S on the x-axis. The area of the rectangle PQRS is A square units. ;;;;Show that $$A=72x-2x^{3} $$. [2];;c) The table below gives some values of x and the corresponding values of A, where $$A=72x-2x^{3} $$.;img;;c-i) Find the value of t. [1];;c-ii) Using a scale of 2 cm to represent 1 unit, draw a horizontal x-axis for $$0\leq x\leq 6$$. Using a scale of 1 cm to represent 20 units, draw a vertical A-axis for $$0\leq A\leq 180$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;c-iii) Use your graph to find the two values of x when A = 108. [2];;c-iv) Find the lengths of the sides of the recAnswers:

ID: 200102002009
Content:
a) Over a 40 day period, the number of students absent from school was recorded. The results are given in the table above.;img;For example, on 8 of the days there were 5, 6, 7, 8 or 9 students absent from school.;;a-i) Which is the modal class? [1];;a-ii) Calculate an estimate of the mean number of students absent per day. [3];;b) The diagram shows the cumulative frequency graph of the marks scored by 160 students in an examination.;img;;b-i) Use the graph to estimate;;b-i-a) the median mark, [1];;b-i-b) the inter-quartile range, [2];;b-i-c) the number of students who scored 70 marks or more. [1];;b-ii) Before combining these marks with those of another exam, the teacher scaled them. To obtain the scaled mark, the teacher multiplied each student;;b-ii-a) the median scaled mark, [1];;b-ii-b) the inter-quartile range of the scaled marks, [1];;b-ii-c) the number of students who had a scaled mark of 80 or more. [2]Answers:

ID: 200102002010
Content:
img;In the diagram, $$\vec{AD}=p$$, $$\vec{DB}=q$$ and $$AC=2AD$$.;;a) Express, as simply as possible, in terms of p and q,;;a-i) $$\vec{AB}$$, [1];;a-ii) $$\vec{CB}$$. [1];;b) E is a point such that $$\vec{BE}=p$$.;;b-i) Express $$\vec{AE}$$ in terms of p and q. [1];;b-ii) Explain why ABEC is a trapezium. [1];;c) Given that |\p|=8, |\q|=7 and $$A \hat DB=57^{\circ}$$, calculate;;c-i) the perpendicular distance from B to AB, [2];;c-ii) the area of the trapezium ABEC, [2];;c-iii) the length of AB. [4]Answers:

ID: 200102002011
Content:
a) A shop sells two packs of fireworks. Pack A contains 15 rockets and 25 fountains. Pack B contains 5 rockets, 20 mines and 10 fountains. The prices of single fireworks are: rockets $2, mines $3, fountains $1. This information can be represented by the matrices P and Q below. ; ; $$P=\begin{bmatrix}15&0&25\\5&20&10\end{bmatrix}, Q=\begin{bmatrix}2\\3\\1\end{bmatrix}$$;;a-i) Find PQ. [2];;a-ii) Explain what the numbers in your answer represent. [1];;b) The inverse of $$\begin{bmatrix}x&-1\\2&0\end{bmatrix}$$ is $$\begin{bmatrix}0&y\\-1&-2\end{bmatrix}$$. Find the values of x and the value of y. [3];;c);img;The diagram shows the triangles X, Y and Z. The single transformation D maps X onto Y. The enlargement E maps X onto Z.;;c-i) Describe D completely. [2];;c-ii) Find the coordinates of the centre of the enlargement E. [2];;c-iii) O is the origin. Find the coordinates of DE(O). [2]Answers:

\end{document}
