\documentclass{article}
\begin{document}
ID: 200103002001
Content:
Find the value of;;a) $$0.2 \times 0.45$$ [1];;b) $$1 \frac{3}{5} \div 2 \frac{1}{3}$$ [1]Answers:

ID: 200103002002
Content:
Find the value of;;a) $$\sqrt{0.0081}$$ [1];;b) $$7^3 \times 7^{-3}$$[1]Answers:

ID: 200103002003
Content:
On four occasions a bus takes the following times to complete a journey. $$1 \frac{2}{3}$$ hours, 1.7 hours, 1 hour 39 minutes, $$1 \frac{3}{4}$$ hours ;By first expressing these times in minutes, write them in order of size, starting with the smallest. [2]Answers:

ID: 200103002004
Content:
img;A mark, M, on a cliff is 1.96 m below sea level at high tide.;At low tide the sea level is 4.18 m lower than at high tide.;;a) How far is M above sea level at low tide? [1];;b) At a certain time the sea level is exactly half way between high tide and low tide. How far is the sea level below M at this time? [1]Answers:

ID: 200103002005
Content:
img;Using the information given in the advertisement shown, find the sale price of the table. [2]Answers:

ID: 200103002006
Content:
a);img;Complete the diagram to make a quadrilateral ABCD which has rotational symmetry of order 2. [1];;b);img;Complete the diagram to make a quadrilateral PQRS which has PR as its line of symmetry. [1]Answers:

ID: 200103002007
Content:
a) Express, correct to two significant figures,;;a-i) 386.71, [1];;a-ii) 0.02049 [1];;b) Hence estimate, correct to one significant figure, the value of $$386.71 \times 0.02049$$ [1]Answers:

ID: 200103002008
Content:
Factorise completely;;a) $$9a - 12a^2$$,    [1];;b) $$4y^2 - 1$$,    [1];;c) $$x^2 - 7x + 12$$.    [1]Answers:

ID: 200103002009
Content:
The population of a country was 13.1 million.;;a) Nine hundred thousand of the population were at least 2 metres tall. How many were less than 2 metres tall?    [1];;b) 0.2% of the population were over 95 years old. How many were over 95?    [2]Answers:

ID: 200103002010
Content:
a) Solve the inequality $$-5 < 2x +3 < 1$$. [2];;b) Write down the largest integer, x, which satisfies $$-5 < 2x + 3 < 1$$ [1]Answers:

ID: 200103002011
Content:
The numbers 168 and 324, written as the products of their prime factors, are $$168 = 2^3 \times 3 \times 7, 324 = 2^2 \times 3^4$$ ;Find;;a) $$\sqrt{324}$$, [1];;b) the largest integer which is a factor of both 168 and 324, [1];;c) the smallest positive integer value of n for which 168n is a multiple of 324.    [1]Answers:

ID: 200103002012
Content:
img;a) A pile of 1500 sheets of paper is 6 cm high.;Find the thickness of one sheet of paper;;a-i) in centimeters, giving your answer as a decimal,    [1];;a-ii) in metres, giving your answer in standard form.    [1];;b) Each sheet of paper is 30 cm long and 20 cm wide. Find the total surface area of both sides of one sheet of paper, giving your answer in square metres.    [1]Answers:

ID: 200103002013
Content:
img;The graph of $$y = (x + 2)(3 - x)$$ cuts the x axis at A and B. It cuts the y axis at C. Find;;a) The coordinates of the point C,    [1];;b) The length AB,    [1];;c) The equation of the straight line AC.    [1]Answers:

ID: 200103002014
Content:
img;The graph is a cumulative frequency curve showing the marks gained by 300 candidates in an examination.;;a) Use the curve to estimate;;a-i) the median mark,    [1];;a-ii) the number of candidates who gained 33 marks or less.    [1];;b) It is given that 70 candidates achieved a grade A. Use the curve to estimate the smallest mark required for a grade A.    [1]Answers:

ID: 200103002015
Content:
y is inversely proportional to (x+2).;;a) Write down an expression for y in terms of x and a constant k.    [1];;b) It is given that y=4 when x=3. Find y when x=8.    [2]Answers:

ID: 200103002016
Content:
a) A car travels 144 km in h hours. Write down, in its simplest form, an expression in terms of h for its average speed in metres per seconds.    [2];;b) Solve the equation 3(2x - 7) = 6 - 4(2 - x) [2]Answers:

ID: 200103002017
Content:
img;A, B and C are three towns.;C is equidistant from A and B.;The bearing of C from A is $$132^{\circ}$$ and $$B \hat AC = 75^{\circ}$$.;Find;;a-i) the acute angle ACB, [1];;a-ii) the reflex angle ACB, [1];;b) the bearing of A from C, [1];;c) the bearing of A from B.    [1]Answers:

ID: 200103002018
Content:
img;The ratio of the areas of the bases of two geometrically similar buckets is 4:9.;;a) The area of the top of the smaller bucket is $$480cm^2$$. What is the area of the top of the larger bucket?    [1];;b) Write down the ratio of the heights of the two buckets.    [1];;c) Both buckets are filled with sand.;The mass of sand in the larger bucket is 36 kg.;Find the mass of sand in the smaller bucket.    [2]Answers:

ID: 200103002019
Content:
a);img;The graph of the line $$y = 2x - 1$$ is shown in the answer space. On the diagram, sketch the graph of;;a-i) y = 2x,;;a-ii) y = 1-2x. [2];;b);img;The point (1, 1) is marked on the diagram in the answer space. On the diagram, sketch the graph of $$y = \frac{1}{x}$$.    [2]Answers:

ID: 200103002020
Content:
a) Given that a=2 and b=-5, find the value of $$ab^2$$.    [1];;b) Solve the equations;;b-i) $$\frac{5}{c} = 12$$,    [1];;b-ii) $$(x + 2)(x - 3) = 14$$.    [2]Answers:

ID: 200103002021
Content:
img;The diagram shows three points A(-2, 7), B(-2, 2) and C(6, -4). Find;;a) the length BC,    [2];;b) the area of triangle ABC,    [2];;c) the value of $$\sin A \hat BC$$.    [1]Answers:

ID: 200103002022
Content:
A car starts from rest and accelerates at a constant rate to a speed of 20 m/s in 10 seconds.;;a) Find the acceleration.    [1];;b) It then travels at a constant speed of 20m/s for the next 10 seconds. ;Find the total distance travelled in the 20 seconds.    [1];;c) On the axes below, draw;;c-i) the speed-time graph for the first 20 seconds of the car;img;;c-ii) the distance-time graph for the same 20 seconds.    [2];img;Answers:

ID: 200103002023
Content:
The diagram below is the scale drawing of a field.;img;In the drawing, 1 cm represents 10 m.;;a) Express the scale in the form 1:n.    [1];;b) Treasure is buried in the field. It is know that the treasure is ;I	within 60 m of C,;;II	nearer to A than C,;III	equidistant from AB and AC.;Use I, II and III to construct the locus of possible positions of the treasure.;Find the extreme positions of this locus and label them $$T_1$$ and $$T_2$$.    [4]Answers:

ID: 200103002024
Content:
An examination is set every month.;John takes the examination each month until he passes.;Each time he takes the examination, the probability that he passes is 0.9.;;a) Find the probability that John;;a-i) fails the first examination and passes the second,    [1];;a-ii) passes the examination in either the first or second month,    [1];;a-iii) fails the first three examinations,    [1];;a-iv) passes the examination in one of the first four months.    [1];;b-i) Find the probability, in terms of n, that John fails the first n examinations.    [1];;b-ii) Write down the probability that John passes the examination in one of the first n months.    [1]Answers:

\end{document}
