\documentclass{article}
\begin{document}
ID: 200201002001
Content:
a) Calculate the value of $$0.1 \times 0.06$$. [1];;b) Find the decimal number exactly halfway between 1.01 and 1.02. [1]Answers:

ID: 200201002002
Content:
Giving the answer as simply as possible, calculate;;a) $$\frac{3}{4}-\frac{1}{3}$$, [1];;b) $$\frac{2}{5}$$ of  $$\frac{15}{16}$$. [1]Answers:

ID: 200201002003
Content:
a) Calculate the value of $$9^{\frac{1}{2}}+9^{0} $$. [1];;b) The reciprocal of $$2^{-3} $$ is $$2^{n}$$. Write down the value of n. [1]Answers:

ID: 200201002004
Content:
a) Calculate the value of $$16-8\div 2$$. [1];;b) Express 0.0032 in standard form. [1]Answers:

ID: 200201002005
Content:
Mr. Smith asked the children in his class ;img;;a);img;By making tally marks, or otherwise, obtain the frequency distribution of the colours. [1];;b) State the mode of this distribution. [1]Answers:

ID: 200201002006
Content:
P is the point (1, 1) and Q is the point (5, -2).;;a) A translation maps P onto Q. Write down the column vector which represents this translation. [1];;b) Find the coordinates of the midpoint of PQ. [1]Answers:

ID: 200201002007
Content:
img;The diagram shows a lighthouse, L, and two ports P and Q. Q is due east of L and $$P \hat LQ=80^{\circ}$$. P and Q are each 10 km from L. Find;;a) $$L \hat QP$$, [1];;b) the bearing of Q from P, [1];;c) the bearing of L from P. [1]Answers:

ID: 200201002008
Content:
Solve the simultaneous equations ;2y = 2x - 13; 5x - 6y = 23;[3]Answers:

ID: 200201002009
Content:
img;There are 50 people on a tour. One day, 26 people went on the morning cruise and 29 to the evening barbecue. Using Venn diagrams, or otherwise, answer the following questions.;;a) It was thought that 4 people went to both events and 1 person to neither. Explain why this was not possible. [1];;b) Find the least number and the greatest number of people who could have gone to both events. [2]Answers:

ID: 200201002010
Content:
Consider the sequence $$1^{3} -2, 2^{3} -4, 3^{3} -6, 4^{3} -8$$, ....;;a) Write down the 5th term of the sequence. [1];;b) Write down, in terms of n, an expression for the nth term of the sequence. [1];;c) Evaluate the 10th term of the sequence. [1]Answers:

ID: 200201002011
Content:
img;The diagram shows triangles A, B and C.;;a) An enlargement maps triangle A onto triangle B. Write down the scale factor of this enlargement. [1];;b) Describe completely the single transformation which will map triangle A onto triangle C. [2]Answers:

ID: 200201002012
Content:
img;The triangle ABC has vertices A(-3, 5), B(3, 5) and C(-3, -1). Write down the three inequalities which define the region inside the triangle ABC. This region does not include points on the boundaries. [3]Answers:

ID: 200201002013
Content:
It is given that $$f:x->m+nx$$, where m and n are constants. Given also that f(0) = 1 and f(4) = 21, find the value of ;;a) m, [1];;b) n, [1];;c) $$f^{-1}(21)$$. [1]Answers:

ID: 200201002014
Content:
In 2000 Esther went to a tennis tournament. Her ticket cost $35. At the tournament she bought a programme costing $3 and an ice-cream costing $2.;;a) This information is to be shown on a pie chart. Calculate the angle of the sector which represents the amount she spent on ice-cream. [2];;b) In 2001 the cost of a ticket was $36.75. Calculate the percentage increase in the cost of a ticket. [2]Answers:

ID: 200201002015
Content:
img;In the diagram, TC, TD and AB are straight lines.;;a) Construct the locus of the points which are equidistant from TC and TD.;;b) Construct the locus of the points which are equidistant from A and B.;;c) The two loci meet at P. AB is a chord of a circle, centre P. Draw the circle. [4]Answers:

ID: 200201002016
Content:
img;Diagram I shows a device for measuring angles in a vertical plane. Diagram II shows the device being used by a surveyor. He views the top of a flagpole at an angle $$x^{\circ}$$ to the horizontal.;;a) Write down the value of x. [1];;b) The surveyor stands on horizontal ground 50 m from the vertical pole. His eye level is 1.8 m above the ground. Using a scale of 1 cm to 5 m, make an accurate scale drawing and use it to find the height of the flagpole. [3]Answers:

ID: 200201002017
Content:
a) Factorize completely 18rc - 3rd - 6tc + td. [2];;b) Solve the equation $$\frac{4}{x+3}=\frac{3}{2x}$$. [2]Answers:

ID: 200201002018
Content:
img;The points A, P, Q, B and S lie on a circle. AP is produce to R. $$R \hat PQ=69^{\circ}$$, $$P \hat BA=24^{\circ}$$ and $$Q \hat SB=21^{\circ}$$.;;a) Find $$Q \hat PB$$, giving your reasons. [1];;b) Given that M is the midpoint of AB, find $$P \hat MA$$. Give all your reasons. [3]Answers:

ID: 200201002019
Content:
img;The cumulative frequency curve shows the distribution of the times of 300 competitors in a women;;a) The race was won by Tegla. Find her time, giving your answer in hours and minutes. [1];;b) Find the median time in hours and minutes. [1];;c) The qualifying time for the Olympic Games was achieved by ten percent of the runners. The race began at 11.30. At what time did the last qualifying athlete finish the race? Express your answer using the 24 hour clock. [2]Answers:

ID: 200201002020
Content:
img;V varies inversely as P. When P = 3, V = 1. ;;a) Express V in terms of P. [2];;b) Complete the table. [2]Answers:

ID: 200201002021
Content:
Given that $$S = \frac{RV}{3V-1}$$,;;a) calculate the value of S when R = 100 and V = -13. [1];;b) express V in terms of R and S. [3]Answers:

ID: 200201002022
Content:
img;The diagram shows the speed-time graph of a bus over a period of 90 seconds. The bus reaches a maximum speed of 15 metres per second.;;a) Express 15 metres per second in kilometers per hour. [1];;b) Given that the acceleration was $$0.5 ms^{-2} $$, calculate the time taken, in seconds, to reach its maximum speed. [1];;c) The total distance travelled during the 90 seconds was 750 metres. Calculate the length of time that the bus was travelling at its maximum speed. [2]Answers:

ID: 200201002023
Content:
A transformation S is represented by the matrix  $$\begin{bmatrix}2&0\\0&1\end{bmatrix}$$. ;;a) The shape A has vertices (1, 0), (0, 1), (-1, 0) and (0, -1). Shape A is shown on the grid.;img; By calculating $$\begin{bmatrix}2&0\\0&1\end{bmatrix}\begin{bmatrix}1&0&-1&0\\0&1&0&-1\end{bmatrix}$$ or otherwise, draw and label the shape S(A). [2];;b) Find the matrix which represents the transformation $$S^{2} $$. [1];;c) On the grid below, draw and label $$S^{2} (A)$$. [1];img;;d) On the grid below, draw and label $$S^{3} (A)$$. [1];img;;e) Write down the matrix which represents $$S^{n}$$. [1]Answers:

ID: 200201002024
Content:
a);img;The diagram shows a 10 cm cube.;;a-i) A triangular pyramid is cut from the corner of the cube at A. The cut is made halfway along each of the edges meeting at A as shown. Calculate the volume, in cubic centimeters, of the pyramid. [The volume of a pyramid = $$\frac{1}{3} \times area.of.base \times height$$] [2];;a-ii);img;From another 10 cm cube, a second similar pyramid is cut from the corner at P. The volume is 8 times the volume of the first pyramid. On the diagram, draw the lines where the cut is made.[1];;b) Another 10 cm cube is cut as shown. A prism containing the corners B and C is removed. Calculate the volume which remains. [2]Answers:

\end{document}
