\documentclass{article}
\begin{document}
ID: 200303002001
Content:
a) Find the fraction which is exactly halfway between $$\frac{1}{7}$$ and $$\frac{4}{7}$$.   [1];;b) Subtract 370 grams from 3.7 kilograms. Give your answer in kilograms.   [1]Answers:

ID: 200303002002
Content:
Express $$7 \frac{1}{2}$$%;;a) as a decimal,   [1];;b) as a fraction in its simplest form.   [1]Answers:

ID: 200303002003
Content:
Evaluate;;a) $$12 \frac{1}{3} - 9 \frac{3}{5}$$,   [1];;b) $$8.4 \div 0.02$$ [1]Answers:

ID: 200303002004
Content:
a) Write down the square root of $$6 \frac{1}{4}$$.   [1];;b) State which of the following numbers are irrational $$\sqrt{2} \times \sqrt{8}, \frac{22}{7}, \pi, 2\sqrt{3}$$. [1]Answers:

ID: 200303002005
Content:
The highest air temperature recorded is $$58.8^{\circ}$$C. The lowest air temperature recorded is $$-89.2^{\circ}$$C.;;a) What is the difference between these two temperatures?   [1];;b) The lowest air temperature recorded in Britain is $$62^{\circ}$$C higher than $$-89.2^{\circ}$$C. Find the lowest air recorded in Britain.   [1]Answers:

ID: 200303002006
Content:
a);img;Find the lowest common multiple of 12, 30 and 66.   [1];;b) Three lightships flash simultaneously at 6 00 a.m.;The first lightship flashes every 12 seconds, the second lightship every 30 seconds and the third lightship every 66 seconds.;At what time will the three lightships next flash together?   [1]Answers:

ID: 200303002007
Content:
a);img;Shade three more squares so that the completed square grid has rotational symmetry of order 4.   [1];;b);img;Shade one more squares so that the completed square grid has one line of symmetry.   [1]Answers:

ID: 200303002008
Content:
a) Write down the following numbers in order of size, starting with the smallest -0.29, -1.5,  0,  -0.3,  -4. [1];;b) The thickness of a sheet of paper is $$8 \times 10^{-4}$$ cm. Find the thickness of two sheets of paper, giving your answer in standard from.   [1]Answers:

ID: 200303002009
Content:
img;The diagram shows part of a regular polygon with n sides. Each interior angle of this polygon is $$156^{\circ}$$.;;Find;;a) the value of n,   [1];;b) angle ACD,   [1];;c) angle ADC.   [1]Answers:

ID: 200303002010
Content:
a) y is directly proportional to $$x^2$$.; It is known that y = 10 for a particular value of x.; Find the value of y when this value of x is halved.   [1];;b) Seven men can paint a bridge in 15 days.;;b-i) How long would it take 3 men?   [1];;b-ii) The bridge was painted in t days. Write down an expression, in terms of t, for the number of men needed to paint the bridge.   [1]Answers:

ID: 200303002011
Content:
img;All the students from two schools, A and B, take the same examination paper. ;The cumulative frequency curves show the results for the two schools.;;a) Estimate the median mark of the students from school A.   [1];;b) Estimate the percentage of the students from school B who gained more than 80 marks.   [1];;c) State, with a reason, which school achieved the better results.   [1]Answers:

ID: 200303002012
Content:
Find a, b and c when;;a) $$3^a \div 3^5 =27$$,   [1];;b) $$125^b = 5$$,   [1];;c) $$10^c = 0.001$$.   [1]Answers:

ID: 200303002013
Content:
Factorise fully $$4ax^2 - 3b + 12bx^2 - a$$ [3]Answers:

ID: 200303002014
Content:
A map is drawn to a scale of 1 : 400 000.;;a) Find the actual distance, in kilometers, represented by 7 centimetres on the map.   [1];;b) A city covers an area of 800 square kilometers. Find, in square centimetres, the area representing the city on the map.   [2]Answers:

ID: 200303002015
Content:
img;The two circles shown have radii x and 3x.;;a) A point is chosen, at random, inside the larger circle. Find, in its simplest fractional form, the probability that this point is in the shaded area.   [2];;b) Find, in its simplest form, the ratio circumference of large circle: sum of circumference of the two circles.   [2]Answers:

ID: 200303002016
Content:
a) Solve $$-8 < 2x + 3 < 11$$. [2];;b) Write down the greatest and least integers which satisfy $$-8 < 2x + 3 < 11$$. [2]Answers:

ID: 200303002017
Content:
img;ABCD is a rectangle.;ABP and BCQ are equilateral triangles.;;a) Prove that angle PBQ = $$90^{\circ}$$.   [1];;b) By proving that two triangles are congruent, show that AC=PQ. Give reasons for each of your statements.   [3]Answers:

ID: 200303002018
Content:
Look at this pattern;;a) Write down;;a-i) the 8th line of this pattern,   [1];;a-ii) the nth line of this pattern.   [1];;b) Use the pattern to find;;b-i) $$340^2 - 339^2$$,   [1];;b-ii) the integers x and y such that $$x^2-y^2=701$$ Answers:

ID: 200303002019
Content:
a-i) Factorise $$ax - bx$$.   [1];;a-ii) Hence evaluate $$1426 \times 0.6789 - 426 \times 0.6789$$ [1];;b) Solve the equation $$3(x - 5) -2 = 7 - (1 - x)$$ [2]Answers:

ID: 200303002020
Content:
img;In the diagram, OABC is a parallelogram, $$\vec{OA} = 4p - q$$ and $$\vec{OC} = p+5q$$.;;a) Express, as simply as possible, in terms of p and q,;;a-i) $$\vec{BC}$$,   [1];;a-ii) $$\vec{AC}$$.   [1];;b) D is the point such that $$\vec{OD} = -p + 2q$$.;;b-i) Explain why $$\vec{AC}$$ is parallel to $$\vec{OD}$$.   [1];;b-ii) Given that the area of triangle OAC is 18 square units, find the area of triangle OCD.   [1]Answers:

ID: 200303002021
Content:
img;In the diagram, angle ABC = angle AED.;;a) Explain why triangle ABC and AED are similar.   [1];;b) Given also that AD = 3 cm, AE = 5 cm and EC = 2 cm, calculate;;b-i) BD   [3];;b-ii) $$\frac{Area.of.triangle.AED}{Area.of.triangle.ABC}$$.   [1]Answers:

ID: 200303002022
Content:
img;The point A(-5, 5), B(1, -3) and C(4, -3) are shown in the diagram. Find;;a) the coordinates of midpoint of AC,   [1];;b) the gradient of the line AB,   [1];;c) the equation of the line which passes through (0, 3) and is parallel to AB,   [1];;d) the length of AB,   [1];;e) the value of cos $$A \hat BC$$.   [1]Answers:

ID: 200303002023
Content:
img;Each of the containers shown in the diagrams has a height of 40 cm. ;Their other dimensions are as shown.;All three containers have uniform cross-sections.;The containers are being filled to the brim with water which flows into each one at the same constant rate.;It takes 12 minutes to fill each container.;;a) Find the time taken for the water to reach a depth of 20 cm in ;;a-i) container B,   [1];;a-ii) container C,   [1];;b) A graph is drawn showing the relationship between the depth of the water, d cm, and the time, t minutes, as each container is being filled.;The graph shown in the answer space is that for container A.;On the same diagram, sketch the graph for;;b-i) container B,;img;;b-ii) container C.   [4]Answers:

ID: 200303002024
Content:
Triangle ABC is drawn below.;img;;a) Measure angle ABC.   [1];;b) The point D is below AC where AD is 12 cm and CD is 9 cm.;Using ruler and compasses only, complete the construction of triangle ADC on the diagram in the answer space.;;c) The region, S, lies within the quadrilateral ABCD.;Points in S are;I.	Nearer to C than A,;II.	More than 8 cm from B,;III.	Nearer to BA than BC.;Using ruler and compasses only, use conditions I, II and III to construct appropriate loci.;Hence shade the region S.   [5]Answers:

\end{document}
