\documentclass{article}
\begin{document}
ID: 200301002001
Content:
a) Express 0.03 as a fraction. [1];;b) Express $150 as a percentage of $500. [1]Answers:

ID: 200301002002
Content:
a) Evaluate $$\frac{7}{8}-\frac{7}{10}$$, giving your answer as a fraction in its lowest terms. [1];;b) Evaluate $$2\frac{1}{3} \times 3\frac{1}{2}$$, giving your answer as a mixed number. [1]Answers:

ID: 200301002003
Content:
Evaluate;;a) $$24\div 6+2 \times 9$$, [1];;b) $$0.4 \times 0.02$$. [1]Answers:

ID: 200301002004
Content:
img;Local time in Singapore is 11 hours ahead of Trinidad.;;a) Look at the two clocks. One shows the local time in Singapore. Show the local time in Trinidad on the other clock. [1];;b) It is 9.15 a.m. in Trinidad. Using the 24 hour clock, write down the local time in Singapore. [1]Answers:

ID: 200301002005
Content:
a) Factorize $$x^{2} -7x+12$$. [1];;b) Solve (x + 1)(3x - 2)= 0. [1]Answers:

ID: 200301002006
Content:
a) Express 99 as the product of its prime factors. [1];;b) Find the smallest possible integer value of n for which 99n is a multiple of 24. [1]Answers:

ID: 200301002007
Content:
a) It is given that $$5^{-2} \times 5^{k}=1$$. Write down the value of k. [1];;b) It is given that $$\sqrt[3]{7} = 7^{m}$$. Write down the value of m. [1]Answers:

ID: 200301002008
Content:
a) Add together 37 kilograms and 40 grams. Give your answer in kilograms. [1];;b) The length of a piece of string is 0.026 metres, correct to the nearest millimeter. Write down, in millimeters, the lower bound of this length. [1]Answers:

ID: 200301002009
Content:
$$p=3.2 \times 10^{11}$$ and $$q=8 \times 10^{-4}$$. Expressing your answers in standard form, evaluate;;a) $$q^{2} $$, [1];;b) $$p\div q$$. [1]Answers:

ID: 200301002010
Content:
$$a=\begin{bmatrix}-2\\4\end{bmatrix}$$, $$b=\begin{bmatrix}-3\\2\end{bmatrix}$$, $$c=\begin{bmatrix}u\\10\end{bmatrix}$$.;;a) Express 2a + b as a column vector. [1];;b) Given that the vector c is parallel to the vector a, calculate the value of u. [1]Answers:

ID: 200301002011
Content:
Solve the simultaneous equations $$4x-y=9$$, $$2x-3y=-23$$. [3]Answers:

ID: 200301002012
Content:
img;Five items bought at a shop are shown on the receipt. The part showing the cost of the apples is missing.;;a) How much did the apples cost? [1];;b);img;The total cost of $5.90 when converted to euros is 6.80 euros.;;b-i) Using these totals, draw a graph on the axes which will enable you to convert dollars ($) to euros. [1];;b-ii) Use your graph to estimate the cost of the mineral water in euros. [1]Answers:

ID: 200301002013
Content:
a) Solve the equation $$\frac{5}{x+1}=4$$. [1];;b) Solve the inequality 7 - y < 9. [1];;c) Write down the least integer value of z for which  z > -4. [1]Answers:

ID: 200301002014
Content:
img;The points A, B, C, D and E lie on the circle with diameter AC. EB and AC meet at F. GA is a tangent to the circle at A. $$C \hat DE = 128^{\circ}$$ and $$B \hat FC = 65^{\circ}$$. Calculate;;a) $$G \hat AE$$, [2];;b) $$A \hat EB$$. [1]Answers:

ID: 200301002015
Content:
img;The lines x + y = 2 and x - 3y = 6 are shown on the diagram.;;a) Find the gradient of the line x - 3y = 6. [1];;b) On the diagram, shade the region defined by the inequalities $$x+y\leq2$$, $$x-3\leq6$$ and $$x+1 \geq 0$$. [2]Answers:

ID: 200301002016
Content:
a) State the order of rotational symmetry of a regular decagon. [1];;b) Write down those letters of the word AMBULANCE which have a vertical axis of symmetry. [1];;c) A and B are two points in space which are 10 cm apart. Describe fully the locus of points in three dimensions that are 3 cm from the line which starts at A and ends at B. [2]Answers:

ID: 200301002017
Content:
A function is defined by $$f(x) = 3x + 4$$.;;a) Given that f(k) = k, find k. [2];;b) Find the inverse of f. [2]Answers:

ID: 200301002018
Content:
a) In a group of language students, 24 studied Spanish, 23 studied French and 15 studied	German, 12 studied Spanish and French, 10 studied German and French, 6 studied Spanish and German, 4 studied all three languages. By drawing a Venn diagram, or otherwise, calculate the number of students who studied;;a-i) both Spanish and French, but not German, [1];;a-ii) only one language. [1];;b) The set A consists of the points whose coordinates (x, y) are given by A={(x,y):y=2x + 1}. The points in set B are given by B={(0,0),(0,1),(1,2),(2,5),(3,6)}. Find;;b-i) n(B), [1];;b-ii) $$A \cap B$$. [1]Answers:

ID: 200301002019
Content:
img;The vertices of the square ABCD lie on a circle of radius r cm.;;a) Show that the length, l cm, of a side of the square is $$r \sqrt{2}$$ cm. [1];;b) By comparing the perimeter of the square and the circumference of the circle, or otherwise, show that $$\sqrt{2} < \frac{\pi}{2}$$. [2];;c) What special kind of numbers are $$\sqrt{2}$$ and $$\pi$$? [1]Answers:

ID: 200301002020
Content:
a) Expand and simplify $$(x-1)(x^{2} +x+1)$$. [2];;b) Factorize ax - bx - 3ay + 3by. [2]Answers:

ID: 200301002021
Content:
img;Two vertical posts of the same height stand on horizontal ground. The distance between the posts is d centimeters. When a wire of length w centimeters is suspended between the posts, the sag in the middle is s centimeters. The sag is given by the formula $$s=\sqrt{\frac{3d(w-d)}{8}}$$.;;a) Find s when d = 800 and w = 803. [1];;b) Express w in terms of d and s. [3]Answers:

ID: 200301002022
Content:
It is given that $$\sin 30^{\circ}=0.5$$ and $$\cos30^{\circ} = 0.866$$.;;a) Write down the value of;;a-i) $$\cos 150^{\circ}$$, [1];;a-ii) $$\cos 60^{\circ}$$. [1];;b) A triangle has sides of length 6 cm and 5 cm. The angle between these two sides is $$150^{\circ}$$. Calculate the area of the triangle. [2]Answers:

ID: 200301002023
Content:
img;In the diagram, $$\vec{OP}=o$$, $$\vec{OQ}=q$$ and $$\vec{OR}=r$$. The midpoints of PQ and QR are E and F respectively.;;a) Express, as simply as possible, in terms of p and/or q,;;a-i) $$\vec{PE}$$, [1];;a-ii) $$\vec{OE}$$. [1];;b) Hence write down $$\vec{OF}$$. [1];;c) Find $$\vec{EF}$$. [1];;d) Write down two facts about EF and PR. [1]Answers:

ID: 200301002024
Content:
img;The speed-time graph shows the performance of a cyclist during the first 90 seconds of a race.;;a) Calculate the acceleration of the cyclist during the first 10 seconds. [1];;b) Calculate the distance, in meters, travelled by the cyclist in the first 90 seconds. [3];;c) Calculate the time taken for the cyclist to travel 1 kilometer. [2]Answers:

ID: 200301002025
Content:
The numbers of goals scored in 20 football matches were 5, 0, 5, 4, 1, 0, 5, 5, 1, 3, 4, 5, 0, 0, 5, 5, 3, 2, 5, 4.;;a-i);img;Complete the table. [1];;a-ii);img;Using the axes, represent the information as a bar chart. [2];;b) State the median. [1];;c) Calculate the mean number of goals. [2]Answers:

\end{document}
