\documentclass{article}
\begin{document}
ID: 200403002001
Content:
a) $$0.4 \times 0.06$$, [1];;b) $$\sqrt[3]{0.008}$$. [1]Answers:

ID: 200403002002
Content:
img;In the answer space, write down the letters of all the shapes which have;;a) exactly 1 line of symmetry, [1];;b) rotational symmetry of order 2. [1]Answers:

ID: 200403002003
Content:
Evaluate;;a) $$1\frac{2}{3}\div 5$$, [1];;b) $$4\frac{1}{4}-1.43$$, giving your answer as a decimal. [1]Answers:

ID: 200403002004
Content:
a) Write down the next two terms in the sequence 20, $$16\frac{1}{2}$$, 13, $$9\frac{1}{2}$$, 6, ...... [1];;b) Write down an expression, in terms of n, for the nth term of the sequence 1, 4, 7, 10, 13, ......  [1]Answers:

ID: 200403002005
Content:
a) Add together 181 centimetres and 14.85 metres. Give your answer in metres. [1];;b) Express 40000 square metres in square kilometers. [1]Answers:

ID: 200403002006
Content:
a) Express $$\frac{17}{40}$$ as a percentage. [1];;b) Evaluate $$(\frac{1}{3})^{-2}$$. [1]Answers:

ID: 200403002007
Content:
img;A block of wood is cuboid, 10 cm by 6 cm by 2 cm. Find;;a) its volume, [1];;b) its surface area. [1]Answers:

ID: 200403002008
Content:
img;In the diagram, BCD is a straight line. BC = 5 cm, AB = 12 cm, AC = 13 cm and $$A \hat BC=90^{\circ}$$. Find;;a) $$\tan B \hat AC$$, [1];;b) $$\cos A \hat CD$$. [1]  Give both answers as fractions.Answers:

ID: 200403002009
Content:
img;The diagram shows the positions of A and B. Find the bearing of;;a) A from B, [1];;b) B from A. [1]Answers:

ID: 200403002010
Content:
a) During one week the temperatures at midnight were $$3^{\circ}C, 4.5^{\circ}C, 1^{\circ}C, -2^{\circ}C, 0^{\circ}C, 6.5^{\circ}C, -3.5^{\circ}C$$. Find the difference between the highest and lowest temperatures. [1];;b) Find all the integers which satisfy both 2x + 7 < 3 and $$x  \geq  4$$. [1]Answers:

ID: 200403002011
Content:
img;The diagram shows the graph of $$y= x^{2} + x -12$$.;;a) The graph cuts the y-axis at K(0, k). Write down the value of k. [1];;b) The graph cuts the x-axis at L(l, 0) and M(m, 0). Find the value of;;b-i) l, [1];;b-ii) m. [1]Answers:

ID: 200403002012
Content:
An atom of helium has a mass of $$6.8 \times 10^{-27}$$ kilograms.;;a) Express this mass in grams. Give your answer in standard form. [1];;b) A room contains $$9 \times 10^{22}$$ atoms of helium. Find the mass of helium in the room. Give your answer in grams as a normal decimal number. [2]Answers:

ID: 200403002013
Content:
$$\vec{AB}= \begin{bmatrix}8\\-4\end{bmatrix}$$, $$\vec{BC}=\begin{bmatrix}6\\4\end{bmatrix}$$.;;a) Express $$\vec{AC}$$ as a column vector. [1];;b) It is given that $$\vec{CD}=\begin{bmatrix}-11\\h\end{bmatrix}$$. Find the two possible values of h which will make ABCD trapezium. You may use the grid below to help you with your investigation. [2];img;Answers:

ID: 200403002014
Content:
a) A man bought a painting for $50. Several years later he sold it at a profit of 350%.	Find the selling price. [1];;b) $400 is invested in an account which pays 10% per year compound interest. Find the total interest earned if the money is left in the account for 3 years. [2]Answers:

ID: 200403002015
Content:
a) p is proportional to $$q^{3} $$. It is known that p = 24 for a particular value of q. Find the value of p when this value of q is halved. [1];;b) y is inversely proportional to $$x^{2} $$. y = 4 when x = 3. Find y when x = 10. [2]Answers:

ID: 200403002016
Content:
Andy has 2x books. Bill has 4 more books than Andy. Carol has half as many books as Bill.;;a) Write down an expression, in terms of x, for the number of books that Carol has. [1];;b) The total number of books is 121. Find the number of books that Bill has. [2]Answers:

ID: 200403002017
Content:
a);img;In the diagram, O is the centre of the circle. Find the value of x. [2];;b);img;The diagram shows a square inscribed in a circle, centre O. The radius of the circle is 6 cm. The perimeter of the shaded region can be written as centimeters. Find the value of p and q. [2]Answers:

ID: 200403002018
Content:
img;ABCD is a rectangle and M is a point of CD. AC and BM meet at X.;;a) Prove that triangles CXM and AXB are similar. [2];;b) It is given that CM = 3MD. Find the ratio;;b-i) area of $$\Delta  CXM$$: area of $$\Delta  AXB$$ [1];;b-ii) area of $$\Delta  BXC$$: area of rectangle ABCD. [1]Answers:

ID: 200403002019
Content:
img;The lengths of 40 nails were measured. Their lengths, in centimeters, are summarized in the table below.;;a) On the axes in the answer space, draw the histogram which represents this information. [2];img;;b) Calculate an estimate of the mean length of the nails. [2]Answers:

ID: 200403002020
Content:
a) The interior angle of a regular polygon is $$160^{\circ}$$. How many sides does it have? [2];;b);img;ABCDE...... is part of a regular polygon which has interior angles of $$160^{\circ}$$. CDLM is a square. Find;;b-i) the value of x, [1];;b-ii) the value of y. [1]Answers:

ID: 200403002021
Content:
img;The diagram shows the distance-time graphs of the journeys of Ali and Bala from home to school. They leave home together and follow the same route. Ali runs to school and Bala cycles.;;a) How long does it take Ali to run the first 700 m? [1];;b) Estimate the distance between Ali and Bala when t = 3. [1];;c) Find Bala;;d) Find BalaAnswers:

ID: 200403002022
Content:
a) Factorize (a - 2b) - 3c(a - 2b). [1];;b) Simplify 5t(t + 3) - 3(5t - 2). [1];;c) Solve the simultaneous equations $$2x - 3y = 15$$, $$3x-7y=27\frac{1}{2}$$. [3]Answers:

ID: 200403002023
Content:
a) A coach left London at 20 45 and arrived in Edinburgh the next day at 05 05. How long does the journey take? [1];;b) The distance between London and Edinburgh is 660 km.;;b-i) A train took 5 hours 30 minutes to complete the journey. Calculate its average speed. [2];;b-ii) The average speed of another train was 150 km/h. How long did this train take for the journey? Give your answer in hours and minutes. [2]Answers:

ID: 200403002024
Content:
img;In triangle ABC, AB = 15 cm, BC = 8 cm and AC = 11 cm. The side AB is drawn in the answer space.;;a) Using ruler and compass only, complete the triangle. [1];;b) Measure the largest angle of the triangle. [1];;c) Using ruler and compass only, draw the locus of all points within the triangle that are;;c-i) 5 cm from C, [1];;c-ii) equidistant from BA and BC. [1];;d) The point P, within the triangle, is such that PC = 5 cm and P is equidistant from BA and BC. Label the point P and measure the distance PA. [1]Answers:

ID: 200403002025
Content:
The diagram below shows the point P and triangles A, B, C and D.;img;;a) The translation T maps $$\Delta  A$$ onto $$\Delta  B$$. Given that T(P) = Q, write down the coordinates of Q. [1];;b) Describe fully the single transformation which maps $$\Delta  A$$ onto $$\Delta  C$$. [2];;c) $$\Delta  A$$ is mapped onto $$\Delta  D$$ by a shear. Write down;;c-i) the equation of the invariant line, [1];;c-ii) the shear factor. [1];;d) $$\Delta  A$$ is mapped onto $$\Delta  E$$ by a rotation of 90o clockwise about the point (4, 2). Draw and label $$\Delta  E$$on the diagram above. [2]Answers:

\end{document}
