\documentclass{article}
\begin{document}
ID: 200404002001
Content:
img;The diagram represents some beams which support part of a roof. AD and BC are horizontal and CDE is vertical. AC = 8 m, $$\vec{BAC}=78^{\circ}$$, $$\vec{ACD}=35^{\circ}$$ and  $$\vec{CAE}=90^{\circ}$$. Calculate the length of the beam;;a) AD, [2];;b) CE, [2];;c) AB. [3]Answers:

ID: 200404002002
Content:
The points A, B and C are (9, 8), (12, 4) and (4, -2) respectively.;;a) Find;;a-i) the gradient of the line through A and B, [1];;a-ii) the equation of the line through C which is parallel to AB. [2];;b) Calculate the length of the line segment;;b-i) AB, [1];;b-ii) BC. [1];;c) Show that AB is perpendicular to BC. [1];;d) Calculate the area of triangle ABC. [1]Answers:

ID: 200404002003
Content:
Mr. Smith bought three companies, Alpha, Beta and Gamma, for a total of $80,000,000. The amounts he paid for these companies were in the ratio 4 : 5 : 7.;;a) Calculate how much he paid for each company. [2];;b) When he sold the companies, he made a profit of 12% on the $80,000,000 he paid for them. Calculate the profit he made on the sale of the three companies. [1];;c) When he sold the companies, he made a profit of 25% on Alpha and a loss of 10% on Beta. Calculate;;c-i) the profit he made on Alpha, [1];;c-ii) the percentage profit that he made on Gamma. [3];;d) When the previous owner, Mr. Jones, sold the companies to Mr. Smith for $80,000,000, he made a profit of 60%. Calculate the total amount Mr. Jones had paid for the companies. [2]Answers:

ID: 200404002004
Content:
img;In the diagram, ABCD is a square. Points P, Q, R and S lie on AB, BC, CD and DA so that AP = BQ = CR = DS.;;a) Giving all your reasons, prove that;;a-i) PB = QC, [2];;a-ii) triangle BPQ is congruent to triangle CQR, [3];;a-iii) PQR is a right angle. [2];;b) Write down two reasons to prove that PQRS is a square. [2]Answers:

ID: 200404002005
Content:
a);img;The diagram shows a circle which passes through D, E and F. AFB, BDC and CEA	are tangents to the circle. D is the midpoint of BC. Given that BD = 5 cm and AE = 8 cm, find;;a-i) EC, [1];;a-ii) $$C \hat AD$$. [2];;b);img;The diagram shows a circle which passes through X, Y and Z. PZQ, QXR and RYP are	tangents to the circle. Given that $$P \hat QR=52^{\circ}$$ and $$Q \hat RP=58^{\circ}$$, calculate;;b-i) $$Q \hat PR$$, [1];;b-ii) $$Q \hat ZX$$, [2];;b-iii) $$Z \hat XY$$. [2]Answers:

ID: 200404002006
Content:
a) It is given that $$S=\frac{n(a+1)}{2}$$.;;a-i) Find the value of S when n = 20, a = -5 and l = 17. [1];;a-ii) Express l in terms of S, n and a. [2];;b) Solve the equations;;b-i) $$5t^{2} =12t$$, [2];;b-ii) $$\frac{y-1}{8}=\frac{2}{y-1}$$. [3];;c) Solve the equation $$3x^{2} +9x+5-0$$, giving both answers correct to two decimal places. [4]Answers:

ID: 200404002007
Content:
img;Three paths, AB, BC and CA, run along the edges of a horizontal triangular field ABC. BC = 51 m, AC = 72 m and angle ACB = $$81^{\circ}$$.;;a) Calculate the length of AB. [4];;b) Calculate the area of the field ABC. [2];;c) Calculate the shortest distance from C to AB. [2];;d) A vertical tree, CT, has its base at C. The angle of elevation of the top of the tree from A is $$15^{\circ}$$. Calculate the height of the tree. [2];;e) John measured the largest angle of elevation of the top of the tree as seen from the path AB. Calculate this angle of elevation. [2]Answers:

ID: 200404002008
Content:
img;The diagram shows the design of a company symbol. It consists of three circles. ; The smallest circle has centre O and radius 2x centimeters. The largest circle has centre O and radius 2y centimeters. The third circle touches both the other two circles as shown. The three regions formed are colored red, yellow and green as shown.;;a) Explain fully why the radius of the third circle is (x + y) centimeters. [2];;b) Write down, in terms of $$\pi$$, x and y expressions for the area of the region that is colored;;b-i) yellow, [1];;b-ii) green. [1];;c) The area of the green region is twice the area of the yellow region. Use this information to write down an equation involving x and y, and show that it simplifies to $$y^{2} -6xy=5x^{2} =0$$. [3];;d-i) Factorize $$y^{2} -6xy+5x^{2} $$. [1];;d-ii) Solve the equation $$y^{2} -6xy+5x^{2}=0$$, expressing y in terms of x. [2];;e) Calculate the fraction of the design that is colored yellow. [2]Answers:

ID: 200404002009
Content:
Three integers, a, b and c, are such that a < b < c. The three integers are said to form a Pythagorean Triple if $$c^{2} =a^{2} +b^{2} $$ or $$c^{2} -b^{2} =a^{2} $$. ; ;For example, ; 3, 4, 5 form a Pythagorean Triple because $$5^{2} -4^{2}  =(5-4)(5+4)= 1 \times 9=3^{2} $$ and ; 5, 12, 13 form a Pythagorean Triple because $$13^{2} -12^{2} =(13-12)(13+12)=1 \times 25 =5^{2} $$.;;a) In the same way, show that 7, 24 and 25 form a Pythagorean Triple. [1];;b) Form a Pythagorean Triple;;b-i) in which the last two integers are 40 and 41, [1];;b-ii) in which the first integer is 11. [1];;c-i) Simplify $$(n+1)^{2} -n^{2} $$. [1];;c-ii) Hence form a Pythagorean Triple in which the first integer is 101. [2];;d) It is also possible to form Pythagorean Triples in which the last two integers differ by 2. ; ; For example, ; 8, 15, 17 form a Pythagorean Triple because $$17^{2} -15^{2} =(17-15)(17+15)=64=8^{2} $$.;;d-i) Copy and complete the following statements:;..., 35, 37 form a Pythago and ..., 63, 65 form a PythagoAnswers:

ID: 200404002010
Content:
img;Answer the whole of this question on a sheet of a graph paper. ;; A solid cylinder of radius r centimeters and height h centimeters has a volume of $$100\pi cm^{3} $$.;;a-i) Show that $$h=\frac{100}{r^{2}}$$. [1];;a-ii) The cylinder has a total surface area of $$\pi$$y square centimeters. Show that $$y=2r^{2} +\frac{200}{r}$$. [1];;b) The table below shows some values of r and the corresponding values of y, correct to the nearest whole number.;img;;b-i) Find the value of p. [1];;b-ii) Using a scale of 2 cm to represent 1 cm, draw a horizontal r-axis for $$1\leq r\leq 6$$. Using a scale of 2 cm to represent $$20 cm^{2} $$, draw a vertical y-axis for $$70\leq y\leq 200$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;c) Use your graph to find the values of r for which y = 100. [2];;d) By drawing a tangent, find the gradient of the graph at the point where r = 2. [2];;e) Use your graph to find;;e-i) the value of r for which y is least, [1];;e-ii) the smallest possible value of the total surface area of the cylinderAnswers:

ID: 200404002011
Content:
Answer the whole of this question on a sheet of graph paper. ;; The table below shows the marks obtained in tests of English and Mathematics by 140 students.;img;;a) Copy and complete the cumulative frequency table below. [2];img;;b) Using a scale of 2 cm to represent 20 marks, draw a horizontal x-axis for $$0\leq x\leq 100$$. Using a scale of 2 cm to represent 20 pupils, draw a vertical axis for values from 0 to 140. On your axes, draw and label both smooth cumulative frequency curves to illustrate this information. [3];;c) Use your curves to find;;c-i) the upper quartile mark for English, [1];;c-ii) the inter-quartile range for English, [1];;c-iii) the median mark for English and the median mark for Mathematics. [1];;d) State, with a reason, which you think is the easier test. [1];;e) One student is chosen at random. It may be assumed that the marks gained in the two subjects are independent. Expressing each answer as a fraction in its lowest terms, calculate the probability ;;e-i) student gains more than 60 marks on both papers;;eii)student gains more than 80 marks on one paper, but not on the otherAnswers:

\end{document}
