\documentclass{article}
\begin{document}
ID: 200504002001
Content:
img;The diagram shows two circles with centres O and P. ABC and ADE are tangents to the circles at B, C, D and E as shown. AOP is a straight line.;;a) Giving a reason for your answer, write down angle ABO. [1];;b) It is given that OB = 6 cm, AO = 13 cm and PC = 15 cm.;;b-i) Show that angle OAB = $$27.5^{\circ}$$, correct to one decimal place. [1];;b-ii) Calculate AC. [2];;b-iii) Calculate CE. [3]Answers:

ID: 200504002002
Content:
a) Solve the equation $$\frac{3t+1}{2}=4$$. [2];;b) Solve the simultaneous equations 2x + y = 12, 3y - 2x = 56. [2];;c) Simplify $$\frac{3y^{2} +8y+4}{y^{2} -4}$$. [3];;d) Given that 3h + 2x = 2f - gx , express x in terms of f, g and h. [3]Answers:

ID: 200504002003
Content:
img;The points A, B, C, D and E lie on a circle. AD is a diameter of the circle. DB bisect angle ADC. Angle ADC = $$56^{\circ}$$.;;a) Giving your reasons, write down;;a-i) angle DCA, [1];;a-ii) angle DAC, [1];;a-iii) angle CBA, [1];;a-iv) angle AEB. [1];;b) It is given that EB is parallel to DC and that EB cuts AD at X. [You must not assume that X is the centre of the circle.] Prove that triangle BDX is isosceles. [2];;c) Find angle EBA. [1];;d) Hence or otherwise prove that X is the centre of the circle. [1]Answers:

ID: 200504002004
Content:
img;The table shows the number of cars owned by each of 25 families.;;a) Draw a dot diagram to represent the information in the table. [2];;b) Find;;b-i) the median number of cars, [1];;b-ii) the modal number of cars, [1];;b-iii) the mean number of cars. [1];;c) A family is chosen at random. Find the probability that it owns 3 cars. [1];;d) Two families are chosen at random. Find the probability that one family owns 2 cars and the other owns 4 cars. [2];;e) A car is chosen at random. Find the probability that it belongs to a family which owns 2 cars. [2]Answers:

ID: 200504002005
Content:
The cost of parking in a car park is $1 for each hour. When he parked his car, John had only a large number of $1 coins and $2 notes to put into the ticket machine. The table shows how he can pay to park his car.;img;;a) Show that there are;;a-i) 5 ways to pay for 4 hours, [1];;a-ii) 8 ways to pay for 5 hours. [1];;b) The table below shows the number of ways John can pay when parking for various times.;img;;b-i) Find the values of a and b. [3];;b-ii) Write down an equation connection x, y and z. [1]Answers:

ID: 200504002006
Content:
A road tanker holds 24 tonnes of oil.;;a) In cold weather it can pump out x tonnes of oil per minute. Write down an expression, in terms of x, for the number of minutes it takes to empty the tanker in cold weather. [1];;b) In hot weather it can pump out (x + 0.5) tonnes of oil per minute. Write down an expression, in terms of x, for the number of minutes it takes to empty the tanker in hot weather. [1];;c) It takes 2 minutes longer to empty the tanker in cold weather than in hot weather. Write down an equation in x, and show that it simplifies to $$2x^{2} +x-12=0$$. [3];;d) Solve the equation $$2x^{2} +x-12=0$$, giving the solutions correct to 3 decimal places. [4];;e) Find the time taken, in minutes and seconds, correct to the nearest seconds, to empty the tanker in cold weather. [2]Answers:

ID: 200504002007
Content:
img;A room has length 3.6 m, width 2.5 m and height 2.2 m. It has one door which is a rectangle of width 0.9 m and height 1.9 m. It has one window which is a rectangle of width 1.2 m and height 0.8 m, with a semicircle on one of its longer sides.;;a-i) Calculate the area of the window. [2];;a-ii) Show that the area of the walls, correct to three significant figures, is $$23.6 m^{2} $$ .[2];;b) Tiles are to be fixed to the walls inside the room. Eileen estimated the number of tiles needed to cover the walls inside the room in the following way. She first increased the area, $$23.6 m^{2} $$, by 12% and then calculated the number of tiles that she needed to cover this total area. Each tile is a square of side 25 cm. ;;b-i) Find the number of tiles that she needed. [3];;b-ii) The tiles are sold in boxes, each containing 20 tiles. Each box of tiles costs $15. Calculate the cost of the boxes of tiles that she bought. [2];;b-iii) When the shopkeeper sold the tiles at $15 per box, he made a profit of 20%. Calculate the profit of each box of tiles.Answers:

ID: 200504002008
Content:
img;Three points A, B and C, lie on a horizontal field. Angle BAC = $$75^{\circ}$$ and the bearing of C from A is 217$$^{\circ}$$. AB = 72 m and AC = 60 m.;;a) Calculate;;a-i) the bearing of B from A, [1];;a-ii) BC, [4];;a-iii) angle ABC, [3];;a-iv) the bearing of C from B. [1];;b) A girl is standing at B is flying kite. The kite, K, is vertically above A. The string, BK, attached to the kite is at $$24^{\circ}$$ to the horizontal. Calculate the angle of elevation of the kite when viewed from C. [3]Answers:

ID: 200504002009
Content:
img;[The surface area of a sphere = $$4 \pi r^{2} $$.] ;[The volume of a sphere = $$\frac{4}{3} \pi r^{3} $$.]; [The area of the curve surface of a cone of radius r and slant height l is $$\pi rl$$.];[The volume of a cone = $$\frac{1}{3} \times  base.area \times height$$.];;A solid cone has a base radius of 5 cm and height 12 cm. A solid hemisphere has a radius of 5 cm. A metal toy is formed by joining the plane faces of the cone and the hemisphere.;;a) Show that the length of the slant edge of the cone is 13 cm. [1];;b) Calculate;;b-i) the surface area of the toy, [4];;b-ii) the volume of the toy. [3];;c) A solid metal cylinder has a radius of 1.5 m and height 2 m. The cylinder was melted down and all of the metal was used to make a large number of these toys. Calculate the number of toys that were made. [4]Answers:

ID: 200504002010
Content:
img;Answer the whole of this question on a sheet of graph paper.;;The area of a rectangular garden, ABCD, is $$100 m^2$$;;a) Taking the length of AB to be x metres, write down expressions, in terms of x, for;;a-i) EF,;;a-ii) BC,;;a-iii) FG. [2];;b) Hence show that the area, y square metres, of the lawn, EFGH is given by $$y=110-5x-\frac{200}{x}$$. [1];;c) The table below shows some values of x and the corresponding values of y, correct to 1 decimal place, where $$y=110-5x-\frac{200}{x}$$. Find the value of p. [1];img;;d) Using a scale of 2 cm to 1 metre, draw a horizontal x-axis for $$4\leq x\leq 10$$. Using a scale of 2 cm to 2 square metres, draw a vertical y-axis for $$40\leq y\leq 48$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;e) By drawing a tangent, find the gradient of the curve where x = 8. [2];;f) Use your graph to find;;f-i) the range of values of x for which the area of the lawn is at least $$44 m^{2} $$, [2];;f-ii) the value of Answers:

ID: 200504002011
Content:
img;A regular hexagon, ABCDEF, has centre O. $$\vec{OA}=a$$ and $$\vec{OB}=b$$.;;a) Express, as simply as possible, in terms of a and/or b,;;a-i) $$\vec{DO}$$, [1];;a-ii) $$\vec{AB}$$, [1];;a-iii) $$\vec{DB}$$. [1];;b) Explain why |a|=|b|=|b-a|. [1];;c) The points X, Y and Z are such that $$\vec{OX}=a+b$$, $$\vec{OY}=a-2b$$ and $$\vec{OZ}=b-2a$$.;;c-i) Express, as simply as possible, in terms of a and/or b,;;c-i-a) $$\vec{AX}$$, [1];;c-i-b) $$\vec{YX}$$. [1];;c-ii) What can be deduced about Y, A and X? [1];;d) Express, as simply as possible, in terms of a and/or b, the vector $$\vec{XZ}$$. [1];;e) Show that triangle XYZ is equilateral. [2];;f) Calculate $$\frac{Area.of.triangle.OAB}{Area.of.triangle.XYZ}$$ . [2]Answers:

\end{document}
