\documentclass{article}
\begin{document}
ID: 200603002001
Content:
Evaluate;;a) 3 + 2(4 - 5), [1];;b) $$1\frac{1}{3} \div 2\frac{1}{2}$$. [1]Answers:

ID: 200603002002
Content:
a) An empty tin has a mass of 330 g. When filled with powder, the total mass is 2.10 kg. Find the mass, in kilograms, of the powder. [1];;b) Express 2.45 hours in minutes. [1]Answers:

ID: 200603002003
Content:
a) Simplify $$25x^{2} \div 5x^{-4}$$. [1];;b) Solve (2x - 3)(x +2) = 0. [1]Answers:

ID: 200603002004
Content:
In an examination, Alan obtained 32 out of 40 marks. In another examination Ben obtained $$\frac{5}{8}$$ of the total marks. Express the mark of each candidate as a percentage. [1]Answers:

ID: 200603002005
Content:
a) Write the following numbers in order of size, starting with the smallest. $$0.7, 0.7^{2} , \frac{7}{11}, \frac{7}{9}$$. [1];;b) In a school election, John received 220 votes. This was 55% of the total number of votes. Find the total number of votes. [1]Answers:

ID: 200603002006
Content:
The temperature at the bottom of a mountain was $$8^{\circ}C$$. The temperature at the top was $$-26^{\circ}C$$. Find;;a) the difference between the two temperature, [1];;b) the mean of the two temperatures. [1]Answers:

ID: 200603002007
Content:
a) Find the fraction which is exactly halfway between $$\frac{5}{9}$$ and $$\frac{8}{9}$$. [1];;b) Estimate the value of $$\sqrt{5000}$$, giving your answer correct to one significant figure. [1];;c) Evaluate $$3^{0} \times 4^{\frac{3}{2}}$$. [1]Answers:

ID: 200603002008
Content:
Written as the product of its prime factors, $$360=2^{3} \times 3^{2} \times 5$$.;;a) Write 108 as the product of its prime factors. [1];;b) Find the lowest common multiple of 108 and 360. Give your answer as the product of its prime factors. [1];;c) Find the smallest positive integer k such that 360k is a cube number. [1]Answers:

ID: 200603002009
Content:
a) Solve $$-7\leq 3x-4<2$$. [2];;b) Write down all the integers which satisfy $$-7\leq 3x-4<2$$. [1]Answers:

ID: 200603002010
Content:
The distance between the Earth to the Sun is e kilometers, where $$e=1.5 \times  10^8$$. The distance from the Sun to Mercury is m kilometers, where $$m=6 \times 10^{7} $$.;;a) Express e : m as the ratio of two integers in its simplest form. [1];;b);img;The diagram shows when the Earth, the Sun and Mercury are in a straight line, with the Sun between the Earth and Mercury. Find the distance from the Earth to Mercury. Give your answer in standard form. [2]Answers:

ID: 200603002011
Content:
Ann, Brian and Carol share the cost of a car. Ann pays $$\frac{2}{5}$$ of the cost, Brian pays $$\frac{1}{3}$$ and Carol pays the rest.;;a) What fraction of the cost does Carol pay? [1];;b) Ann pays $1600 more than Brian. Find the total cost of the car. [2]Answers:

ID: 200603002012
Content:
img;In the diagram, $$\vec{OA}=4a$$, $$\vec{OC}=2c$$ and $$\vec{CB}=a$$.;;a) Express $$\vec{BA}$$ in terms of a and c. [1];;b) $$\vec{OP}=2a-\frac{4}{3}c$$. Explain why $$\vec{OP}$$ is parallel to $$\vec{BA}$$. [1];;c) Find $$\frac{Area.of.triangle.OBA}{Area.of.triangle.OPA}$$ . [1]Answers:

ID: 200603002013
Content:
img;The 7 sided polygon in the diagram has 6 angles of $$x^{\circ}$$ and one of $$y^{\circ}$$.;;a) Draw the line of symmetry on the diagram. [1];;b) If y = 126, calculate the value of x. [2]Answers:

ID: 200603002014
Content:
Amy either walks or cycles to school each morning. The probability that she walks is $$\frac{2}{3}$$. When she walks, the probability that she is late is $$\frac{1}{9}$$. When she cycles, the probability that she is late is $$\frac{4}{9}$$. Find the probability that on a particular morning,;;a) Amy walks and is not late, [1];;b) she is late. [2]Answers:

ID: 200603002015
Content:
img;The points A and B lie on the circumference of a circle, centre O. The area of the circle is $$81\pi $$;;a) the radius of the circle, [1];;b) the length of the minor arc, giving your answer in the form $$k \pi$$, [2];;c) the acute angle AOB. [1]Answers:

ID: 200603002016
Content:
a) Given that $$(3x-1)(x+p)=3x^{2} +qx-2$$, find the value of;;a-i) p, [1];;a-ii) q. [1];;b) Write down the coordinates of the points where the curve y = (2x + 1)(x - 5) meets	the x-axis. [1]Answers:

ID: 200603002017
Content:
a) y is proportional to $$x^{n}$$. Write down the value of n when;;a-i) $$y cm^{2} $$ is the area of a circle of radius x cm, [1];;a-ii) y hours is the time taken to travel a distance x km at a constant speed. [1];;b) The force, F, between two particles is inversely proportional to the square of the distance between them. The force is 36 units when the distance between the particles	is r metres. Find the force when the distance is 3r metres. [2]Answers:

ID: 200603002018
Content:
img;In the diagram, AB is parallel to DC, and AC and BD meet at X.;;a) Prove that triangles ABX and CDX are similar. [2];;b) AB = 8 cm, AX = 4 cm and XC = 6 cm.;;b-i) Find CD. [1];;b-ii) Given also that BD = 14 cm, find BX. [2]Answers:

ID: 200603002019
Content:
img;In the diagram, the points A, B, C and D lie on a circle, centre O. AOD is a diameter, OB is parallel to DC and $$B \hat OD=140^{\circ}$$. ;;a) x, [1];;b) y, [1];;c) z, [1];;d) t. [1]Answers:

ID: 200603002020
Content:
img;A solid cone, C, is cut into two parts, X and Y, by a plane parallel to the base. ; The lengths of the sloping edges of the two parts are 3 cm and 2 cm. Find the ratio of;;a) the diameter of the bases of X and C, [1];;b) the areas of the bases of X and C, [1];;c) the volumes of X and Y. [2]Answers:

ID: 200603002021
Content:
img;The diagram is the speed-time graph for the first 20 seconds of a journey.;;a) Find;;a-i) the acceleration when t = 16, [1];;a-ii) the distance travelled in the first 20 seconds. [1];;b) On the grid in the answer space, sketch the distance-time graph for the same journey. [3];img;Answers:

ID: 200603002022
Content:
img;The triangle with vertices A(4, 4), B(-2, -6) and C(4, -1) is shown in the diagram. Find;;a-i) the area of $$\Delta ABC$$, [1];;a-ii) the coordinates of the point P such that ABCP is a parallelogram, [1];;a-iii) the area of the parallelogram ABCP, [1];;a-iv) tan $$B \hat AC$$. [1];;b) It is given that the length of BC = k units. Write down cos $$B \hat CA$$, giving your answer in terms of k. [1]Answers:

ID: 200603002023
Content:
The diagram below is a map showing a coastline ABC, a lighthouse L and a point P.;img;The map is drawn to a scale of 1 cm to 100 m. Ships must not sail within 200 m of the coastline nor within 200 m of the lighthouse.;;a) Construct the locus of points 200 m from the lighthouse L. [1];;b) Construct the locus of points 200 m from the coastline ABC. [2];;c) Two ships sail from point P on bearings of $$\theta_1^{\circ}$$ and $$\theta_2^{\circ}$$, such that $$\theta_1 - \theta_2 \geq 10$$. Both ships passed between B and L without breaking the 200 m limits. Find one possible pair of values for $$theta_1^{\circ}$$ and $$theta_2^{\circ}$$. [2]Answers:

ID: 200603002024
Content:
img;The diagram shows triangles T, B and C.;;a) The enlargement, with centre (0, 0) and scale factor 2, maps $$\Delta  T$$ onto $$\Delta  A$$. Draw $$\Delta  A$$ on the diagram above. [1];;b) Describe fully the single transformation which maps $$\Delta  T $$ onto $$\Delta  B$$. [2];;c) A reflection maps $$\Delta  T$$ onto $$\Delta  C$$. Write down the equation of the line of reflection. [2]Answers:

\end{document}
