\documentclass{article}
\begin{document}
ID: 200703002001
Content:
a) Calculate 9 - 2 (10 - 8.8). [1];;b) The figure in the answer space contains three straight lines. Add one straight line so that the completed figure has one line of symmetry. [1];img;Answers:

ID: 200703002002
Content:
In a theatre, $$\frac{1}{5}$$ of the audience were under the age of 50, $$\frac{1}{4} $$ were over 75 and $$\frac{1}{3}$$ of those over 75 were men. Find the fraction of the whole audience that were;;a) between 50 and 75 inclusive, [1];;b) women over 75. [1]Answers:

ID: 200703002003
Content:
a) Express $$\frac{5}{8}$$ as a percentage. [1];;b) Write the following in order of size, starting with the smallest. ; 40%, 0.3, $$\frac{1}{3}$$, $$\frac{2}{7}$$. [1]Answers:

ID: 200703002004
Content:
Correct to 3 significant figures, some cube roots are given in the table below.;img;Using as much information in the table as necessary, write down;;a) $$\sqrt[3]{0.9}$$ , [1];;b) the length of an edge of a cube which has a volume of $$9000cm^3$$. [1]Answers:

ID: 200703002005
Content:
img;In the diagram, O is the centre of the circle. The tangents at A and C meet at T. Find;;a) x, [1];;b) y. [1]Answers:

ID: 200703002006
Content:
a) Write down the 12th term in the sequence 25, 22, 19, 16, ...... [1];;b) Write down an expression, in terms of n, for the nth term in the sequence 9, 16, 25, 36, ...... [1]Answers:

ID: 200703002007
Content:
The length of each side of a square is increased by 20%. Find the percentage increase in the area of the square. [2]Answers:

ID: 200703002008
Content:
a) Evaluate $$(\frac{1}{2})^{-3} $$. [1];;b) Given that $$a^{4} \times a \div  \sqrt{a} =a^{k}$$, find the value of k. [1]Answers:

ID: 200703002009
Content:
img;A rectangular picture is 16 cm long and 10 cm wide. It has a 2 cm border around it, as shown in the diagram. ; Calculate the area of the border, giving your answer in;;a) square centimeters, [1];;b) square millimeters. [1]Answers:

ID: 200703002010
Content:
img;In quadrilateral ABCD, the interior angle A is acute, AB > AD and the interior angle C is reflex. The side AD is drawn in the answer space. Complete one possible quadrilateral. [2]Answers:

ID: 200703002011
Content:
The points P and Q are (-3, 1) and (5, -5) respectively. Find;;a) the midpoint of PQ, [1];;b) the length of the line PQ. [1]Answers:

ID: 200703002012
Content:
img;In the triangle ABC, angle ABC = $$90^{\circ}$$ and BC is produced to D.;;a) Write down $$\cos A \hat CD$$. [1];;b) Calculate the perpendicular distance from B to AC. [1]Answers:

ID: 200703002013
Content:
A shop sells two sizes of wheelbarrows which are geometrically similar. The ratio of the lengths of the wheelbarrows is 2 : 3.;;a) The diameter of the wheel of the small wheelbarrow is 30 cm. Find the diameter of the wheel of the large wheelbarrow. [1];;b) The large wheelbarrow holds 135 litres of wet cement. Find how much wet cement the small wheelbarrow can hold. [2]Answers:

ID: 200703002014
Content:
img;a) Estimate the percentage of the figure that is shaded. [1];;b) For a wedding reception, with 334 guests, the caterers charge $59.95 per person. By approximating both the charge and the number of guests to 2 significant figures, estimate the cost of catering for the reception. Show your working and give your answer to a reasonable degree of accuracy. [2]Answers:

ID: 200703002015
Content:
A class of 11 boys and 9 girls took a test. The girls;;a) Find the mean mark for the girls. [1];;b) The mean mark for the boys was 6.0. Find the mean mark for the whole class. [2]Answers:

ID: 200703002016
Content:
img;The two triangles in the diagram are similar.;;a) State the angle equal to angle AEC. [1];;b) Given that AB = 12 cm, BC = 3 cm and CD = 5 cm, calculate DE. [2]Answers:

ID: 200703002017
Content:
img;The diagram is the distance-time graph for the first 25 seconds of a car;;a) Find the speed of the car when t = 15. [1];;b) The car moved with a constant acceleration for the first 10 seconds. Find this acceleration. [1];;c) On the grid in the answer space, draw the speed-time graph for the same journey. [2];img;Answers:

ID: 200703002018
Content:
img;a)The graph of $$y=3-12x^{2} $$ intersects the y-axis at A and the x-axis at B and C. Write down the coordinates of A, B and C. [2];;b);img;The sketch represents the graph of y = $$x^{n}$$. Write down a possible value of n. [1];;c) Write down a possible equation for this graph. [1]Answers:

ID: 200703002019
Content:
The force of attraction, F newtons, between two magnets is inversely proportional to the square of the distance, x centimeters, between them.;;a) When the magnets are 4 cm apart, the force is 3 newtons. Find the formula connection F and x. [2];;b) Find the force when the magnets are 2 cm apart. [1];;c) When the magnets are a certain distance apart, the force is 1.25 newtons. Write down the force when the distance is halved. [1]Answers:

ID: 200703002020
Content:
a) Calculate the time it takes a bullet to travel 100 m at a speed of 5000 m/s. Give your answer in seconds. [1];;b) Calculate the average speed of an insect which travels 450 cm in $$1\frac{1}{2}$$ minutes. Give your answer in metres per second. [2];;c) Light takes $$2\frac{1}{3}$$ minutes to travel from Mars to the Earth. The speed of light is 300000 km/s. Calculate the distance, in kilometers, from Mars to the Earth. [2]Answers:

ID: 200703002021
Content:
The quadrilateral ABCD is drawn in the answer space below.;img;;a) Construct the locus of all points, inside the quadrilateral, which are;;(i)	equidistant from AB and AD, [1];(ii) equidistant from C and B, [1];(iii) 4 cm from the line CD. [1];;;b) The diagram is a scale drawing of a park. The scale is 1 cm to 20 m. A seat is to be placed in the park so that it is equidistant from AB and AD, nearer to C than B and more than 80 m from CD.;;b-i) On the diagram, label with an S one possible position of the seat. [1];;b-ii) Given that x metres is the distance of the seat from A, complete the statement in the answer space. [1]Answers:

ID: 200703002022
Content:
img;Use as much information from the table as necessary to answer the following.;;a) Find the ratio of the population of Singapore to the population of Australia. Give your answer in the form 1 : n. [1];;b) How many more people live in Malaysia than in Singapore? Give your answer in standard form. [2];;c) Calculate the average number of people per square kilometer in the UK. [2]Answers:

ID: 200703002023
Content:
img;The diagram shows the arcs AB and CD of two circles, centre O, with radii 4 cm and 8 cm respectively. OAC and OBD are straight lines and angle COD = $$60^{\circ}$$. Calculate;;a) the perimeter of the shaded region, giving your answer in the form $$a+b\pi$$, [2];;b) the area of the shaded region, giving your answer as a multiple of $$\pi$$, [2];;c) the ratio of the shaded area to the area of the sector AOB. Give your answer in the form m : n where m and n are integers. [1]Answers:

ID: 200703002024
Content:
a) Solve $$(2x-5)^{2} =49$$. [2];;b) Factorize 3xy - 2ab - ay +6xb. [2];;c) Solve 7 - 2x > x + 1. [2]Answers:

ID: 200703002025
Content:
img;The diagram shows the point P(1, 2) and triangles A, B and C.;;a) The translation, T, maps $$\Delta  A$$ onto $$\Delta  B$$. Write down the column vector representing T. [1];;b) An anticlockwise rotation maps $$\Delta  A$$ onto $$\Delta  C$$.;;b-i) Write down the coordinates of the centre of rotation. [1];;b-ii) On the diagram, draw the path that P would follow under this anticlockwise rotation. [1];;c) The enlargement, E, has centre (0, 1) and scale factor -3. Write down the coordinates of E(P). [1];;d) The shear, S, with the x-axis invariant and scale factor 2, maps $$\Delta  B$$ onto $$\Delta  D$$. Draw $$\Delta  D$$ on the diagram. [2]Answers:

\end{document}
