\documentclass{article}
\begin{document}
ID: 200704002001
Content:
The normal price of a roll of film for 36 photographs is $8.99. The normal price of printing 36 photographs is $17.65 for each roll of film.;;a) Show that the cost of each photograph is 74c. [2];;b) Shop A offered every 4th roll of film to be printed free. What is the price of each photograph? ;;c) Shop B kept the price of each roll of film at $8.99. It offered 20% reduction off the normal price for printing the photographs. Sue bought one roll of film at Shop B and had the photographs printed there. Calculate how much each photograph cost her, correct to the nearest cent. [2];;d) Ali decided to buy 4 rolls of film at Shop A and have his photographs printed at Shop B. Calculate the percentage reduction in the cost of each of his photographs compared with the cost in (a). [3]Answers:

ID: 200704002002
Content:
a-i) Simplify $$n^{2} -(n+a)(n-a)$$. [1];;a-ii) Hence evaluate $$326541829^{2}-326541833 \times 326541825$$. [1];;b) Solve the simultaneous equations 2x = y + 6, 6x - 2y = 13. [3];;c) It is given that $$y=t^{2} -2$$.;;c-i) Find y when t = -3. [1];;c-ii) Express t in terms of y. [1];;d) Express as a single fraction in its simplest form $$\frac{5}{3x} - \frac{1}{6x}$$  . [2]Answers:

ID: 200704002003
Content:
img;The diagram shows a parallelogram, ABCD. APQ, BRQ, CRS and DPS are straight lines which bisect angles A, B, C and D respectively. ;;a) Show that angle PAD = angle RCB. [1];;b) Prove that triangles ADP and CBR are congruent. [3];;c) Show that;;c-i) $$D \hat P A = 90^{\circ}$$, [2];;c) $$P \hat Q R=90^{\circ}$$. [2]Answers:

ID: 200704002004
Content:
img;A photocopier prints pages in either ;;a) In one minute it prints x pages in black and white. Write down an expression, in terms of x, for the number of seconds it takes to print one page in black and white. [1];;b) In one minute it prints 2 more copies in black and white than it does in color. Write down an expression, in terms of x, for;;b-i) the number of pages it prints in color in one minute, [1];;b-ii) the number of seconds it takes to print one page in color. [1];;c) It takes 1.5 seconds longer to print one page in color than it takes to print one page in black and white.;;c-i) Write down an equation in x to represent this information, and show that it reduces to $$x^{2} -2x-80=0$$. [3];;c-ii) Solve the equation $$x^{2} -2x-80=0$$. [2];;c-iii) Find the time taken to print 30 pages in color. [2]Answers:

ID: 200704002005
Content:
In the pentagon ABCDE, angles BCD, BDA and AED are each $$90^{\circ}$$ and the angle ADE is $$18^{\circ}$$. CD = 5 cm, BD = 6 cm and AD = 14 cm. Calculate;;a) angle CDB, [2];;b) AE, [2];;c) the radius of the circle through A, B and D. [2]Answers:

ID: 200704002006
Content:
img;The diagram shows a concrete slab, ABCDEF, in the form of a right angled triangular prism. DE = 50 cm, AE = 150 cm and AB = 180 cm.;;a) Calculate the volume, in cubic metres, of the block. [3];;b) The concrete is a mixture of cement, sand and stones in the ratio 3 : 5 : 6 by volume. Show that, correct to three significant figures, the volume of cement needed to make the slab is $$0.145 m^{3} $$. [2];;c) The mass of 1 cubic metre of cement is 1420 kg. Calculate the mass of cement needed to make the slab. [2];;d) Cement is sold in bags, each of which contains a 25 kg of cement. How many bags of cement should be bought to make the block? [2];;e) The price of each bag of cement is $8.50, which includes 5% Goods and Services Tax. Calculate, correct to the nearest cent, the total tax paid for the cement bought to make the slab. [3]Answers:

ID: 200704002007
Content:
img;In the diagram, the rectangle ABCD represents a vertical cliff face. The bottom of the cliff, AB, runs from West to East, and is at sea level. A yacht is in the sea at Y. Angle BAY = $$75^{\circ}$$, angle AYB = $$63^{\circ}$$ and AB = 35 m.;;a) Find the bearing of Y from B. [2];;b) Show that BY = 37.9 m, correct to three significant figures. [2];;c) Calculate the area of triangle ABY. [2];;d) Calculate the shortest distance from the yacht to the cliff. [2];;e) The angle of depression of the yacht when viewed from C is $$18^{\circ}$$.;;e-i) Find the height of the cliff. [2];;e-ii) Calculate the greatest possible value of the angle of elevation of the top of the cliff when viewed from the yacht. [2] Answers:

ID: 200704002008
Content:
a) Show that each interior angle of a regular pentagon is $$108^{\circ}$$. [2];;b);img;The diagram shows a star with its five points, A, B, C, D and E, equally spaced around	a circle, centre O. The chords AC, BD, CE, DA and EB cut one another at P, Q, R, S and T.;;b-i) Describe fully all of the symmetries of the diagram. [3];;b-ii) Showing your working, calculate;;b-ii-a) angle BAC, [2];;b-ii-b) angle CAD, [1];;b-ii-c) angle CQP. [1]Answers:

ID: 200704002009
Content:
img;a) The points L is (3, -2) and the point M is (9, 6).;;a-i) Find the gradient of the line LM. [1];;a-ii) Find the equation of the line LM. [2];;a-iii) Express $$\vec{LM}$$ as a column vector. [1];;a-iv) The point N is such that $$\vec{MN}=4 \vec{LM}$$ and O is the origin. Find the column vector $$\vec{ON}$$. [2];;b) In the diagram, $$\vec{OA}=a$$, $$\vec{OB}=b$$, $$\vec{AP}=\frac{1}{4}\vec{AB}$$ and $$\vec{BC}=3 \vec{OA}$$.;;b-i) Express each of the following in terms of a and b,;;b-i-a) $$\vec{OC}$$, [1];;b-i-b) $$\vec{AP}$$, [1];;b-i-c) $$\vec{OP}$$. [1];;b-ii) What can you deduce about O, P and C? [1];;b-iii) Find $$\frac{Area.of.\Delta OAP}{Area.of.\Delta OBP}$$. [2]Answers:

ID: 200704002010
Content:
img;Answer the whole of this question on a sheet of graph paper. A stone was thrown from the top of a vertical tower. Its position during the flight is represented by the equation $$y=50+21 x-x^{2}$$, where y metres is the height of the stone above the ground and x metres is its horizontal distance from the foot of the tower.;;a-i) Solve the equation $$0=50+21x-x^{2}$$, giving both answers correct to one decimal place. [4];;a-ii) Explain briefly what the positive solution of this equation represents [1];;b) Some corresponding values of x and y are given in the following table. Using a scale of 2 cm to represent 5 metres, draw a horizontal x-axis for $$0\leq x\leq 25$$. Using a scale of 2 cm to represent 20 metres, draw a vertical y-axis for $$0\leq y\leq 180$$. On your axes, plot the points given in the table and join them with a smooth curve. [3];;c) Use your graph to find the greatest height reached by the stone. [1];;d-i) By drawing a tangent, find the gradient of the graph at the point where x = 16. [2]Answers:

ID: 200704002011
Content:
a) The masses of 150 men were measured. The cumulative frequency curve below shows the distribution of their masses.;img;;a-i) Use the curve to estimate;;a-i-a) the median mass, [1];;a-i-b) the upper quartile mass, [1];;a-i-c) the inter-quartile range. [1];;a-ii) It was stated that 18% of these men were considered overweight. Find the least mass for a man to be considered overweight. [2];;a-iii) Use the curve to draw up a table to show the number of men whose masses, w kilograms, fall into each of the intervals of width 10 kg, starting with the interval $$40<w\leq 50$$. On a sheet of graph paper, draw a histogram to represent the distribution of masses. [3];;b) A pack of 16 cards contains 4 cards of each of the colors red, blue, green and yellow.	The four cards of each color are numbered 1, 2, 3 and 4.;;b-i) The pack is shuffled and one card is drawn at random. Find, as a fraction, the probability that it is a red card numbered 4 or a blue card. [1];;b-ii) The card is replaAnswers:

\end{document}
