\documentclass{article}
\begin{document}
ID: 200804002001
Content:
a) Simplify ; $$\frac{7p^2 - 28}{p^2 + 2p}$$;;b) Express as a single fraction in its simplest form, ; $$1 - \frac{3f - g}{f + 2g}$$;;c-i) Express $$x^2 + 11x - 15$$ in the form ; $$(x + a)^2 + b$$;;c-ii) Hence solve the equation $$x^2 + 11x - 15 = 0$$, giving your answers correct to two decimal places.Answers:

ID: 200804002002
Content:
img;A rectangular advertising hoarding, ABCD, is strengthened by three struts, AQ, AP and PQ. ; AQ =9.4 m, AP = 12.1 m, angle PAQ = $$32^{\circ}$$ and angle QAD = $$49^{\circ}$$ Calculate;;a) AD;;b) PB;;c) The area of trangle APQ;;d) PQAnswers:

ID: 200804002003
Content:
In 2006 the cost of making a souvenir was 90 cents.;;a) Find the total cost of making 25 000 souvenirs.;;b) The cost of making each souvenir was divided between materials, wages and other expenses in the ratio of 5:4:6 respectively. ; Find the cost of materials and the cost of wages needed to make each souvenir.;;c) John worked 7 hours per day for 5 days making souvenirs. ; He received a wage of $630 for this week. Calculate the number of souvenirs that he made in one hour.;;d) In 2007 the cost of materials increased by 50% and wages by 10%. ; The other expenses remained the same. ; Giving your answer correct to 3 significant figures, calculate the percentage increase in the total cost of making a souvenir.;;e) A shopkeeper sold a souvenir for $2.00. He made a profit of 25% on the price he paid for it. Calculate how much he paid for the souvenir.Answers:

ID: 200804002004
Content:
The first four terms in a sequence of numbers, $$u_1$$, $$u_2$$, $$u_3$$,$$u_4$$, ..., are given below. ; $$u_1 = 2^0 + 1 = 2$$ ; $$u_2 = 2^1 + 3 = 5$$ ; $$u_3 = 2^2 + 5 = 9$$ ; $$u_4 = 2^3 + 7 = 15$$;;a) Write down an expression for $$u_5$$ and show that $$u_5 = 25$$;;b) Write fown an expression $$u_6$$ and evaluate it.;;c) Write down an expression, in terms of n, for the nth term, $$u_n$$, of the sequence.;;d) Evaluate $$u_{20}$$;;e-i) Show that $$2^{n-1} - 2^{n-2} = 2^{n-2}$$.;;e-ii) Find, and simplify, an expression, in terms of n, for $$u_n - u_{n-1}$$.Answers:

ID: 200804002005
Content:
A trader bought m apples for $12.;;a) Find an expression in terms of m for the cost, in cents of each apple.;;b) It was found that 3 of the apples were bad, and could not be sold. The trader sold each remaining apple for 2 cents more than she paid for it. ; Write down an expression in terms of m, for the total sum she received from the sale of the apples.;;c) She made a profit of 96 cents from the sale of apples. Write down an equation to represent this information and show that it simplifies to ; $$m^2 - 51m - 1800 = 0$$.;;d) Solve the equation $$m^2 - 51m - 1800 = 0$$.;;e) Find the selling price of each apple.Answers:

ID: 200804002006
Content:
img;The diagram shows a a circle, centre O. ; The chords AB and CD intersect at L. ; Angle ALD = $$90^{\circ}$$.;;a) Show that triangles LAD and LCB are similar.;;b) N is the midpoint of BC ; Angle OCD = $$18^{\circ}$$ and angle DAB = $$58^{\circ}$$. ; Find;;b-i) Angle CNO, ;;b-ii) Angle CBA;;b-iii) Angle CON;;b-iv) Angle ADOAnswers:

ID: 200804002007
Content:
a);img;The diagram shows part of a circle, centre O, passing though A and B. ; C is the midpoint of AB. AB = 80 cm and OC = 50 cm. A window is in the form of a minor segment of the circle, as shaded in the diagram;;a-i) Calculate angle AOB in radians;;a-ii) Calculate the area of the windows;;b);img;In the diagram, DEFG represents a rectangular door frame. DXYG represents a rectangular door which can turn about DG and fits into the door frame. The door is opened through $$38^{\circ}$$ as shown. ; DE = DX = 80 cm and DC = 200 m. ; Calculate;;b-i) The length of the straight line EX,;;b-ii) Angle FDYAnswers:

ID: 200804002008
Content:
img;Diagram I shows a pencil. ; It is made up of a cylinder and a cone. ; The cylinder has radius 0.4 cm and height 16 cm. ; The cone has base radius 0.4 cm and height 2 cm.;;a) Calculate;;a-i) The slant height of the cone,;;a-ii) The total surface area of the pencil.;;b) Calculate the volume of the pencil.;;c);img;Diagram II shows twelve of these pencils which just fit into a box;;c-i) Show that the volume of the inside of the box is $$138.24 cm^3$$;;c-ii) Calculate the percentage of the volume of the box that is not occupied by the pencils.Answers:

ID: 200804002009
Content:
Answer the whole of this question on a sheet of graph paper. ; The variables x and y are connected by the equation ; $$y = \frac{1}{5}x(12 - x^2)$$ ; Some corresponding values of x and y are given in the following table. ;img;;a) Find the value of p.;;b) Using a scale of 2 cm to 1 unit, draw a horizontal x-axis for $$-3 \leq x \leq 4$$. ; Using a scale of 2 cm to 1 unit, draw a vertical y-axis for $$-4 \leq y \leq 4$$ ; On your axes, plot the points given in the table and join them with a smooth curve.;;c) Use your graph to find two solutions of $$\frac{1}{5}x(12 - x^2) = 1$$ in the range $$-3 \leq x \leq 4$$.;;d) By drawing a tangent, find the gradient of the curve at the point (3, 1.8).;;e) On the same axes, draw the graph of 2x = y = 2 for $$-1 \leq x \leq 3$$.;;f-i) Write down the x coordinate of the point where the two graphs intersect.   [1];;f-ii) This value of x is a solution of the equation $$x^3 + Ax + Bx + X = 0$$. ; Find the value of A, the value of B and the value of C.Answers:

ID: 200804002010
Content:
a) The total mass of the tomatoes produced by each of 40 tomato plants was measured.; The cumulative frequency curve below shows the distribution of the masses;img;;a-i) Copy and complete the grouped frequency table of the mass of tomatoes on each plant.;;a-ii) Using your grouped frequency table, calculate an estimate of ;;a-ii-a) The mean mass of tomatoes produced by each plant,;;a-ii-b) The standard deviation.;;a-iii) The tomatoes produced by another group of 40 plants have the same median but a larger standard deviation ; Describe how the cumulative frequency curve will differ from the given curve.;;b) A bag contains six identical balls number 1, 2, 3, 4, 5 and 6. Two balls are drawn at random, one after the other, from the bag without replacement.;;b-i) Draw the possibility diagram to show the outcome of the draw;;b-ii) Find, as a fraction in its simplest form, the probability that ;;b-ii-a) Both balls have an even number;;b-ii-b) The sum of numbers drawn is 8;;b-ii-b)Another ball is drawn and at least one of the balls drawn is a multiple of 3Answers:

\end{document}
