\documentclass{article}
\begin{document}
ID: 200903002001
Content:
a) Factorise 20xy - 5y.;;b) Simplify 4x - 4(x + 3)Answers:

ID: 200903002002
Content:
Eriko bought a watch for $48. When he sold it he made a profit of 135% of his cost. Find the selling price.Answers:

ID: 200903002003
Content:
The distribution of colour of cars in a car park is shown in the table. ;img;;a) Write down the modal colour.;;b) This distribution is to be shown in a pie chart. Calculate the angle representing the colour green.Answers:

ID: 200903002004
Content:
a) In a test Jean gained 17 marks out of 24. ; Express this mark as a percentage.;;b) In an examination $$\frac{1}{3}$$ of the candidates were awarded an A grade and $$\frac{1}{4}$$ of the candidates a B grade. ; Find the fraction of candidates who were not awarded an A or B grade.Answers:

ID: 200903002005
Content:
a) Given that $$2p \times 5 = 40$$, find p,;;b) Simplify $$1 \div x^{-4}$$Answers:

ID: 200903002006
Content:
img;In the diagram, AB is parallel to ED and EA is parallel to DC. ; Given the angles shown, find;;a) x,;;b) y,Answers:

ID: 200903002007
Content:
Solve the inequalities $$-2 < 2x - 5 < 7$$.Answers:

ID: 200903002008
Content:
David invests $5000 in a saving account which pays compound interest at the rate of 4.8% per year. Calculate the total interest earned in 6 years.Answers:

ID: 200903002009
Content:
img;The diagram shows a prism whose cross-section is an isosceles triangle. AB = AC = 7.43 cm, $$\angle BAC = 38^{\circ}$$ and the length of the prism is 20 cm. Calculate;;a) The area of the triangle ABC,;;b) The volume of the prism.Answers:

ID: 200903002010
Content:
The first term in a sequence is 38. ; Each following term is found by subtracting 7 from the previous term.;;a) Write down the second and third terms;;b) Write down an expression in terms of n, for the nth term.Answers:

ID: 200903002011
Content:
Two different sizes of tins of soup are shown below. ;img; The mass of the soup and the price are given on the tins. ; Which size of tin gives the better value? ; You must show all your working clearly. ; The ..................... tin gives better value.Answers:

ID: 200903002012
Content:
img;The diagram is the speed-time graph for a car;;a) The acceleration during the first 40 seconds,;;b) The total distance travelled.Answers:

ID: 200903002013
Content:
img;A contrainer is a prism with a triangular cross-section. ; The container has a height of 24 cm. ; Water is poured into the empty container at a constant rate. ; It takes 8 seconds to fill the container. After t seconds the depth of the water is d cm.;;a) Find the values of t when d = 12;;b) On the axes in the answer space, sketch the graph showing how the depth varies during the 8 seconds;imgAnswers:

ID: 200903002014
Content:
img;The diagram shows a toy made from a cone and a hemisphere. ; The cone and the hemisphere both have radius 2.8 cm. ; The cone has a slant height of 7.2 cm. ; Calculate the surface area of the toyAnswers:

ID: 200903002015
Content:
The volume of two gold spheres are $$640 cm^3$$ and $$1250 cm^3$$.;;a) Find, in its simplest form, the ratio of;;a-i) The smaller radius to the larger radius,;;a-ii) The smaller surface area to the larger surface area;;b) The larger sphere has a mass of 25 kg. ; Find the mass of the smaller sphere.Answers:

ID: 200903002016
Content:
a);img;In the kite ABCD, AD = CD = 8 cm. $$\angle ADC = 60^{\circ}, \angle DCB = 130^{\circ}$$ and AB = CB.;;a-i) Write down the length of AC.;;a-ii) Find $$\angle ABC$$;;b);img;O is the centre of the circle though P and Q. ; The tangent at P meets QO produced at T. $$\angle TQP = 32^{\circ}$$. Find;;b-i) $$\angle PQT$$.;;b-ii) $$\angle OTP$$Answers:

ID: 200903002017
Content:
a) One solution of $$2x^2 + kx - 15 = 0$$ is x = 3. ; Find;;a-i) The value of k.;;a-ii) The other solution of the equation;;b) Factorise fully $$6p^2 - 3pq - 10ap + 5aq$$.Answers:

ID: 200903002018
Content:
a);img;Express 150 as the product of its prime factors;;b);img;Find the HCF of 150 and 48.;;c) Bread rolls are sold in packs of 48. ; Chocolate bars are sold in packs of 150. ; John buys the same number of bread rolls as chocolate bars. ; Find the least number of packs of chocolate barsAnswers:

ID: 200903002019
Content:
img;a-i) Calculate $$\frac{494.6}{56.33 \times 98.12}$$, showing all the figures on your calculator display.;;a-ii) Give your answer correct to 1 decimal place.;;b) Sue is trying to estimate the distance across a river from A to B. She paces out the distance from B to C as 280 m and measures angle ACB as $$30^{\circ}$$. Calculate AB, giving your answer to a reasonable degree of accuracy.Answers:

ID: 200903002020
Content:
img;The cumulative frequency graph shows the distribution of marks of 800 students in a Mathematics examination;;a) Find the median mark.;;b) Find the interquartile range.;;c) To be awarded a Grade A, a student has to get a mark of 78 or more. ; Estimate the number of students who are awarded a Grade A.Answers:

ID: 200903002021
Content:
img;Using information from the able above;;a) Find how many more people live in China than Africa, giving your answer in standard form;;b) Calculate the average number of people per square kilometer living in Africa,;;c) Express, in the form 1 : n, the ratio ; number of people living in Singapore : number of people living in ChinaAnswers:

ID: 200903002022
Content:
img;a) A and B lie on the circle centre O, of radius 10 cm. $$\angle AOB$$ = 2.3 radians. Find the length of major arc AB;;b) Find two values of x, in radians, such that $$sin x = \frac{1}{2}$$Answers:

ID: 200903002023
Content:
img;a) Using the information shown in the diagrams, write down two equations in x and y.;;b) Solve these equations to find the value of x and the value of y.Answers:

ID: 200903002024
Content:
img;In the quadrilateral ABCD, the diagonals AC and BD intersect at X. ; AX = DX and BX = CX.;;a) Show that triangles ABC and DCX are congruent.;;b) Name two other triangles that are congruent.;;c) Name two triangles that are similar but not congruent. Answers:

ID: 200903002025
Content:
img;On the axes shown, A is (0, 1), B is (6, 3) and C is (0, -2). Find;;a) The gradient of AB;;b) The equation of the line AB;;c) The area of triangle ABC;;d) The coordinates of two possible points D, such that the four points A, B, C and D are the four vertices of a parallelogram.Answers:

ID: 200903002026
Content:
img;The position vectors of A and B, relative to O, are 6a and 6b respectively. ; $$\vec{OL} = \vec{LA}$$ and $$\vec{BM} = \frac{1}{3} \vec{BA}$$;;a) Express each of the following in terms of a and b;;a-i) $$\vec{BM}$$;;a-ii) $$\vec{OM}$$;;a-iii) $$\vec{ML}$$;;b) Find the position vector of P, such that $$ \vec{LP} = 3 \vec{ML}$$;;c) Make two statements about the points, O, B and P.;;d) Find the position vector N such that LMBN is a parallelogram.Answers:

\end{document}
