\documentclass{article}
\begin{document}
ID: 201004002001
Content:
img;The diagram shows a field, ABCD, which is crossed by two paths, DM and DB. DM is perpendicular to AB and DB is perpendicular to BC. ; DM = 43 m, DB = 72 m, angle BDA = $$62^{\circ}$$ and angle BCD = $$23^{\circ}$$.;;a) Calculate;;a-i) MB, ;;a-ii) AB,;;a-iii) CD;;b) B is due east of A. ; Calculate the bearing of D from B.Answers:

ID: 201004002002
Content:
a) Solve the equation $$\frac{x}{8} = \frac{50}{x}$$.;;b) It is given that $$\frac{t + q}{4} = \frac{q}{5}$$. ; Express t in terms of p and q.;;c) When x copies of a book are printed, the cost, $y, of each copy is given by the formula ; $$y = a + \frac{600}{x}$$, where a is a constant. ; When 50 copies are printed, each costs $17.;;c-i) Find a.;;c-ii) Find the cost of each copy when 100 copies are printed.;;c-iii) Find the total cost of printing 300 copies.;;c-iv) If each copy costs $5.20, how many copies were printed?Answers:

ID: 201004002003
Content:
a) The cash price of a new computer is $1299. Alan buys this computer on hire purchase. ; He pays a deposit of one third of the cash price followed by 24 monthly installments of $40.30.;;a-i) What is the total amount that Alan will pay for the computer?;;a-ii) Find the extra cost of buying the computer on hire purchase as a percentage of the cash price.;;b) Betty buys an identical computer. ; To pay for it, she borrows the whole cost of $1299 for 3 years at compound interest of 6% per year. ; Calculate how much interest Betty will pay.;;c) Carol bought at digital camera for $759 from a trader. ; When Carol bought the camera, the trader made a profit of 15% of the price he paid for it. ; Calculate how much the trader paid for it.Answers:

ID: 201004002004
Content:
The points A, B and C are the vertices of a triangle. The point A is (-5, 4) and the gradient of the line AB is $$\frac{4}{3}$$.;;a) Find the equation of the line AB.;;b) The equation of the line BC is 2x + 9y = 68. ; Find the coordinated of B.;;c) It is given that $$\vec{AE}$$ is $$\begin{bmatrix}6\\1\end{bmatrix}$$.;;c-i) Calculate $$\mid\vec{AE}\mid$$;;c-ii) Find the coordinates of E.;;c-iii) Given also that D is (4, 2), express as a column vector;;c-iii-a) $$\vec{DE}$$;;c-iii-b) $$\vec{DB}$$;;c-iv) What two facts can be deduced about D, E and B?Answers:

ID: 201004002005
Content:
img;The diagram shows part of a regular polygon ABCDEF............, which has 15 sides. ; BCX and EDX are straight lines.;;a) Showing your working, find;;a-i) Angle XCD.;;a-ii) Angle CXD;;b) Explain why XB = XE. ;;c) Showing your working, find angle BEF.Answers:

ID: 201004002006
Content:
John and Peter took part in a marathon race. ; They each ran 42 km.;;a) John ran at a constant speed of x kilometers per hour, ; Write down an expression, in terms of x, for the number of hours he took. ;;b) Peter ran at a constant speed which was $$\frac{1}{2}$$ km/h less than John; Calculate the time taken;;c) The difference between their times was 10 minutes. ; Write down an equation in x to represent this information, and show that it reduces to $$2x^2 - x - 252 = 0$$;;d) Solve the equation $$2x^2 - x - 252 = 0$$, giving the answers correct to three decimal places.;;e) Calculate the time that John took to complete the race, giving your answer in hours, minutes and seconds.Answers:

ID: 201004002007
Content:
imgThe diagram shows a park, PQRS, and a path PR. ; PQ = 95 m, QR = 102 m and PR = 170m;;a) Calculate angle PQR.;;b) A bird is at B, which is 23 m vertically above P. ; Calculate the angle of depression of Q from B.;;c) It is also given that the area of triangle PRS is $$5200 m^2$$; Calculate RS;;d);img;A fence is to be erected along RS. ; This fence is formed by using panels up to 3 metres long supported by post. ;;d-i) Find the number of panels that need to be bought;;d-ii) Each panel costs $28.50 and each post costs $14.95. ; Calculate the total cost of the panels and posts.Answers:

ID: 201004002008
Content:
a);img;The cross-section of a tunnel, shaded in the figure above, is a major segment of a circle centre O and radius 8 m. ; The total perimeter of the major sector POQR is 44m. ; Calculate;;a-i) The magnitude, in radians, of reflex angle POQ,;;a-ii) The area of triangle POQ,;;a-iii) The total area of cross-section of the tunnel.;;b);img;A traffic bollard consists of a pyramid, VABCD attached to a cuboid ABCDEFGH, ; ABCD and EFGH are square of side 10 cm. ; The vertical height, VN, of the pyramid is 12 cm, and VA = VB = VC = VD. ; AE = BF = CG = DH = 30 cm. Calculate;;b-i) The volume of the bollard, ;;b-ii) The surface area of the bollard. ; [Do not include the area of the bottom of the bollard.]Answers:

ID: 201004002009
Content:
Answer the whole of this question on a sheet of graph paper. ; Elizabeth recorded the mass of her new baby every 7 days. ; The table below shows some of the values she recorded.;img;;a) Using a scale of 2 cm to represent 10 days, draw a horizontal axis for $$0 \leq -t \leq 70$$. ; Using a scale of 4 cm to represent 1 kg, draw a vertical m-axis for $$2 \leq m \leq 6$$. ; On your axes, plot the points given in the table and join them with a smooth curve.;;b) Use your graph to estimate;;b-i) The mass of the baby after 63 days,;;b-ii) When the baby;;b-iii) When the baby regain its birth mass.;;c-i) By drawing a tangent, find the gradient of the curve at (7, 3.10).;;c-ii) What does this gradient represent?;;d) Elizabeth wishes to estimate what the mass of the baby will be when it is 1 year old. ; She proposes to extend the graph line up to t = 365. ; Explain why it is not possible to estimate the baby in this way.Answers:

ID: 201004002010
Content:
The sixty member of a group of pupils were asked how many books they had read this term. ; The results of this survey are summarized in the table below. ;img;;a) Find;;a-i) The values of a, b, c, d and e,;;a-ii) The mean and standard deviation of the number of books read.;;b) Find the probability that one pupil chosen at random from the group had read exactly 6 books.;;c) Two pupils are chosen at random from the group. ; Find the probability that both had read more than 4 books.Answers:

\end{document}
